### 2014-04-24 PlatePaper.tex
initial draft commit

%\documentclass[11pt]{amsart}
%\documentclass[5p,twocolumn]{elsarticle}
\documentclass[preprint,review,12pt]{elsarticle}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{color}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{epstopdf}
\usepackage{etoolbox}
\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xfrac}
\usepackage{import}
\usepackage[section]{placeins}

\usepackage{cleveref}
%\usepackage{autonum}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\graphicspath{ {../} }
\graphicspath{ {./images/} }
\newcommand{\diagrampath}{./diagrams}
\newcommand{\plotpath}{./plots}

\newcommand{\mathbi}[1]{\mathit{\mathbf{#1}}}

\newcommand\vstate[3]{%
	\mathbf{\underline{#1}}%
	\ifstrempty{#2}{}{[#2]}%
	\ifstrempty{#3}{}{\langle #3 \rangle}}

\newcommand\tvstate[3]{%
	\mathbf{\underline{#1}\vphantom{\hat{\underline{#1}}}}%
	\ifstrempty{#2}{}{[#2]}%
	\ifstrempty{#3}{}{\langle #3 \rangle}}

\newcommand\sstate[3]{%
	\mathit{\underline{#1}}%
	\ifstrempty{#2}{}{[#2]}%
	\ifstrempty{#3}{}{\langle #3 \rangle}%
	}

\journal{International Journal of Solids and Structures}

\begin{document}

\begin{frontmatter}

\title{Peridynamic Plates and Flat Shells: A non-ordinary, state-based model}

\author[utsa]{James O'Grady\corref{cor1}}
\ead{jogrady@gmail.com}

\author[utsa]{John Foster\corref{cor2}}
\ead{john.foster@utsa.edu}

\cortext[cor1]{Principal Corresponding author}
\cortext[cor2]{Corresponding author}

\address[utsa]{The University of Texas at San Antonio, One UTSA Circle, San Antonio, TX 78249}

\begin{abstract}
This paper builds on the peridynamic state based beam model to represent the bending of a Kirckhoff-Love plate.
This model is non-ordinary and derived from the concept of a rotational spring between bonds.
A simple extension of the beam model reproduces plate bending with a poisson ratio of \(\nu=\sfrac{1}{3}\), which can be combined with a 2D linear peridynamic solid model to simulate mixed in-plane and transverse loading.
The addition of an isotropic bending state term extends the model to arbitrary poisson ratios.
Simple test cases demonstrate the model's performance.
\end{abstract}

\begin{keyword}
peridynamics \sep non-ordinary model \sep non-local model
\end{keyword}

\end{frontmatter}

\section{Introduction}
A goal of many mechanical engineering analyses is the prediction and description of material failure.
When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.  
A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement (as opposed to gradients of displacement), so that discontinuities can evolve naturally and require no special treatment.  
Various peridynamic material models capture the deformation behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would be prohibitively expensive in a computational setting for a long, slender structural object.  
Other peridynamic models capture tension and compression in 1D bars\cite{silling2003deformation} and 2D membranes\cite{silling2005peridynamic}, but these features do not resist transverse displacement.  
A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness. 
This creates a model that can represent thin structures and includes a bending term, but is used to simulate tension loading. 
The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
A nonlocal plate model by Ansari et al. \cite{ansari2010nonlocal} applies Eringen elasticity to Mindlin plate theory, an approach which captures scale effects but imposes stricter continuity requirements.

Instead of developing new equations of motion, previous work by the authors of this article took a different approach, developing a constitutive model that directly resists bending while maintaining the same conservation of momentum equation as the 3D model.
The resulting bending model was shown to reproduce Euler-Bernoulli beam bending based on either linear elasticity or Eringen elasticity.

This paper extends the author's previous work on 1D beams to model the bending of a flat Kirckhoff-Love plate.
The resulting 1-parameter model is constrained to a poisson ratio \(\nu=\sfrac{1}{3}\).
The model is combined with an extension-based model to capture the impact of in-plane forces on bending behavior.
By introducing an isotropic bending state, the model is extended to any valid poisson ratio.
In addition to directly modeling a thin flat plate in bending, the simple plate case lays the theoretical framework for more complex peridynamic plate and shell bending models.
Because many analyses of interest are partly or wholly comprised of these types of features, their development is an important addition to the capabilities of peridynamic analysis.

The second section of this paper provides a brief introduction to peridynamics, including state based models.
The third section presents the state based plate model and demonstrates equivalence to 1-parameter classical Kirckhoff-Love plate theory in the limit of shrinking nonlocality.
Also in the third section, the bending model is combined with an extension-based model to resist both in-plane and out-of-plane deformations.
The fourth section introduces the isotropic bending state and extends the plate to arbitrary poisson ratios.
The fifth section demonstrates the model with simple test cases.
%
\section{Peridynamics}
\label{sec:PDintro}
The term \textit{peridynamic} alludes to the fact that the force at a point is affected by nearby material configuration and was coined by Silling to describe the new formulation of continuum mechanics he developed in \cite{silling2000reformulation}.
Weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.
These higher-order derivatives impose stronger continuity requirements than the classical model. 
By contrast, the peridynamic model is strongly nonlocal and casts material behavior at a point as the \textit{integral} equation 
%
\begin{equation}
    \label{eq:PDCoPV}
    \rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega \mathbi{f}(\mathbf{x},\mathbf{q}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}) \notag
\end{equation}
%
rather than the classical \textit{partial-differential equation}.
Instead of the divergence of stress, we have the integral of a ``force" function $\mathbi{f}$ of the position vector $\mathbf{x}$ and the position vector $\mathbf{q}$ of a point within the body domain $\Omega$. 
This force functional may depend on \(\mathbf{x}\), \(\mathbf{q}\), their deformed positions, the original and deformed positions of other points in \(\Omega\), history, etc.

Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.  While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic}.

To describe force functionals that incorporate the behavior of a totality of points in the nearby material (not just $\mathbf{x}$ and $\mathbf{q}$), we must introduce the concept of a peridynamic state.

Introduced by Silling et al.\ in 2007~\cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.
The most common states are scalar-states and vector-states which are scalar and vector valued, respectively.
Unlike a second order tensor, which can only map vectors linearly to other vectors, vector-states can produce nonlinear or even discontinuous mappings.  Important properties of states are magnitude and direction, while important operations include the addition and decomposition of states, inner and tensor products, and the Fr\'{e}chet derivative of a function with respect to a state \cite{silling2007peridynamic}.

Conservation of linear momentum in the \textit{state-based} peridynamic formulation results in the equation of motion,
%
\begin{equation}
    \label{eq:PDstateEoM}
    \rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega (\vstate{T}{\mathbf{x}}{\mathbf{q}-\mathbf{x}}-\vstate{T}{\mathbf{q}}{\mathbf{x}-\mathbf{q}}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}),\notag
\end{equation}
%
in which $\vstate{T}{\;}{\;}$ is a \textit{force vector-state} that maps the vector in angle brackets, $\langle \rangle$, originating at the point in square brackets, [ ], to a force vector acting on that point.
The deformed image of the vector $(\mathbf{q-x})$ is defined as the \textit{deformation vector-state}, usually denoted $\vstate{Y}{}{}$ and formulated as shown in \cref{eq:PDdeformation} for a displacement field \(\mathbf{u}\). 
%
\begin{equation}
    \label{eq:PDdeformation}
    \vstate{Y}{\mathbf{x}}{\mathbf{q}-\mathbf{x}} = (\mathbf{q}-\mathbf{x}) + (\mathbf{u}(\mathbf{q})-\mathbf{u}(\mathbf{x}))
\end{equation}
%

Just as stress and strain are work conjugate, so too are the force and deformation vector states for hyperelastic materials.
If the force state $\vstate{T}{}{}$ is always in the same direction as the deformation state $\vstate{Y}{}{}$, then the force exerted by a ``bond'' between points is in the same direction as the deformed bond, and the model is called \textit{ordinary}.  
Models in which they are not in the same direction are called \textit{non-ordinary}.
Silling et al. demonstrate the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.
Foster et al. \cite{foster2010viscoplasticity} and Warren et. al. \cite{warren2009non} show that correspondence models, which approximate the deformation gradient and use it to calculate bond forces, result in non-ordinary state based constitutive models for deformation with large rotation.
%
%\FloatBarrier
\section{Model Development}
Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond vector emanating from a point is connected by a rotational spring to its opposite emanating from that same point.
These points and bonds are illustrated in the context of a plate in \cref{fig:BondPairPlate}.
%
\begin{figure}[h]
    \centering
    \subinputfrom{\diagrampath/}{simpleBondPair.eps_tex}
    \caption{Illustration of a bond pair model that resists angular deformation}
    \label{fig:SimpleBondpair}
\end{figure}
%
If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} by taking the Fr\'echet derivative. For the derivation and a description of the Fr\'echet derivative see \ref{sec:frechet}.
%
\begin{align}
\label{eq:SillingForceNO}
\vstate{T}{}{\boldsymbol{\xi}} &= \nabla w\!\left(\vstate{Y}{}{\boldsymbol{\xi}}\right)\notag \\
%
&=\omega(\boldsymbol{\xi})\frac{-\alpha}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \left[\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|} \times \frac{\vstate{Y}{}{-\boldsymbol{\xi}}}{|\vstate{Y}{}{-\boldsymbol{\xi}}|}\right]
\end{align}
%
Though it looks complex, \cref{eq:SillingForceNO} indicates a bond force perpendicular to the deformed bond and in the plane containing both the deformed bond and its partner as illustrated in \cref{fig:Bondpair}. 
The moment that resists the change in angle between partner bonds is proportional to the sine of the angle between them, therefore the force magnitude is proportional to the sine of the angle between the bonds divided by the length of the deformed bond. 
%
\begin{figure}[h]
    \centering
    \subinputfrom{\diagrampath/}{continuousPlate.eps_tex}
    \caption{Illustration of a bond pair on a plate}
    \label{fig:BondPairPlate}
\end{figure}
%
%
\begin{figure}[h]
    \centering
    \subinputfrom{\diagrampath/}{bondPairV.eps_tex}
    \caption{Deformation and force vector states}
    \label{fig:Bondpair}
\end{figure}
%
This response is consistent with the idea of a rotational spring between bonds as long as the change in angle is small. 
Because the potential energy and force states are functions of \textit{pairs} of peridynamic bonds, we will call this formulation a \textit{bond-pair model}. 
Other choices for the bond-pair potential function, such as \( w = (\pi - \theta)^2 \), are also possible, but result in more mathematically complex analysis.
\subsection{Energy Equivalence}
%
To determine an appropriate choice of $\alpha$, we desire our peridynamic model to have an equivalent strain energy density to a classical Kirckhoff plate in the \emph{local limit}, i.e. when the nonlocal length scale vanishes.  
We will begin with the assumptions from Kirckhoff plate theory: straight lines normal to the mid-surface remain both straight and normal to the deformed mid-surface, and plate thickness that does not change with deformation. 
While we will start with the original assumptions from Kirchoff-Love plate theory of small displacements and rotations, they will not constrain the validity of the model for larger displacements and rotations. 
For small vertical displacements we have
%
\begin{equation}
    \theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) \approx \pi-\frac{z(\mathbf{x}+\boldsymbol{\xi})-2z(\mathbf{x})+z(\mathbf{x}-\boldsymbol{\xi})}{|\boldsymbol{\xi}|},
    \label{eq:beamdtheta}
\end{equation}
%
where $z$ is the vertical displacement of material point.  
Taking \(\boldsymbol{\xi}=\xi (\cos(\phi),\sin(\phi))\) in cartesian coordinates and momentarily assuming continuous displacements for the sake of comparison, we use a Taylor series to expand the right-hand-side of eq.~(\ref{eq:beamdtheta}) about \(\xi = 0\) 
%
\begin{equation}
    \theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) \approx \pi-\frac{\xi}{2} \left(\cos^2(\phi) \kappa_1+\sin^2(\phi) \kappa_2+2\sin(\phi)\cos(\phi)\kappa_3\right)+\mathcal{O}(\xi^3)
    \label{eq:beamdtheta2}
\end{equation}
%
with
%
\begin{equation}
    \kappa_1=\frac{\partial^2 z}{\partial x_1^2}, \kappa_2= \frac{\partial^2 z}{\partial x_2^2}, \kappa_3=\frac{\partial^2 z}{\partial x_1\partial x_2}\notag
\end{equation}
%
substituting eq.~(\ref{eq:beamdtheta2}) into the equation for the strain energy density of a single bond-pair,
%
\begin{align}
%\label{eq:continuousBeamw}
    w =& \omega(\boldsymbol{\xi}) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) ) \right] \notag \\
    =& \omega(\boldsymbol{\xi}) \alpha\frac{\xi^2}{8}(\kappa_1^2\cos^4(\phi)+\kappa_2^2\sin^4(\phi)+2\kappa_1\kappa_2\cos^2(\phi)\sin^2(\phi)+4\kappa_3^2\cos^2(\phi)\sin^2(\phi) \notag \\
    & +4\kappa_1\kappa_3\cos^3(\phi)\sin(\phi)+4\kappa_2\kappa_3\cos(\phi)\sin^3(\phi))+\mathcal{O}(\xi^4).\notag
\end{align}
%
If we use a weighting function \(\omega(\boldsymbol{\xi})=\omega(\xi)\) and assume that the $\omega$ plays the role of a localization kernel, i.e. $\omega = 0 \; \forall \; \xi > \delta$, the resulting strain energy density, $W$, for any material point in the peridynamic plate is
%
\begin{align}
    W =& \alpha \int_{0}^\delta\int_0^{2 \pi} w\; \xi {\rm d}\phi {\rm d}\xi ,\notag \\
    =& \alpha \frac{3\pi}{8} \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)\int_{0}^\delta \omega(\xi)\xi^3{\rm d}\xi + \mathcal{O}(\delta^6).\notag 
\end{align}
%
Equating $W$ with the classical Kirchoff plate strain-energy density, $\Omega$, and taking the limit as $\delta \to 0$ we can solve for $\alpha$
%
\begin{align}
    \lim_{\delta \to 0}  W &= \Omega, \notag \\
    \alpha \frac{3 \pi}{8} m \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)&= \frac{G h^3}{12(1-\nu)} \left(\kappa_1^2+\kappa_2^2+2\nu\kappa_1\kappa_1+2(1-\nu)\kappa_3^2 \right), \notag \\
%    \nu = \frac{1}{3},\:\: \alpha &= \frac{8}{3 \pi m} \frac{G h^3}{12(1-\nu)},
    \nu = \frac{1}{3},\:\: \alpha &= \frac{16}{3 m} \frac{G h^3}{12(1-\sfrac{1}{3})},
\label{eq:alpha}
\end{align}
%
with 
\begin{equation}
%    m = \int_{0}^{\delta} \omega(\xi) \xi^3 {\rm d}\xi \notag.
    m = \int_{0}^{\delta} \int_{0}^{2\pi}\omega(\xi) \xi^2 \xi {\rm d}\phi {\rm d}\xi \notag.
\end{equation}

It must be noted that the restriction \(\nu=\sfrac{1}{3}\) is the same imposed by the use of a bond based peridynamic model for in-plane deformation of a 2D peridynamic plate.

\subsection{Combining Bending and Extension Models}
The bond-pair bending model does not resist deformations that preserve the angles between opposite bonds, such as in-plane stretch or shear.
If these behaviors are expected in combination with bending, a useful model must resist both.
To create a plate model that also resists these deformations, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from \cite{silling2000reformulation}.
In this model, individual bonds act as springs resisting changes in length.
%
\begin{equation}
    \label{eq:bondextension}
    \vstate{T}{}{\boldsymbol{\xi}} =\beta\left(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|\right)\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{|\vstate{Y}{}{\boldsymbol{\xi}}|}
\end{equation}
%
By matching the energy of a plate in shear deformation, we can relate \(\beta\) to the shear modulus and thickness of the plate.
Following the example of \cite{silling2007peridynamic}, we begin with a plate under pure in-plane shear.
In Einstein notation, the strain energy of this plate is
%
%\begin{align*}
%    W^d_\text{C} &= G \; h \; \epsilon_{ij} \epsilon_{ij} = G \; h \; \epsilon_{ij}^d \epsilon_{ij}^d \\
%    W^d_\text{PD} &= \frac{\beta}{2}(\underline{\omega}\; \underline{\epsilon^d})\bullet \underline{\epsilon^d}\\
%    &=\frac{\beta}{2} \epsilon_{ij}^d \epsilon_{kl}^d \int_A \frac{\underline{\omega}\langle\xi\rangle}{|\boldsymbol{\xi}|^2}\xi_i \xi_j \xi_k \xi_l \;dA_\xi\\
%\end{align*}
%
\begin{align*}
    W_\text{C} &= G \; h \; \epsilon_{ij}^d \epsilon_{ij}^d \\
    W_\text{PD} &= \frac{\beta}{2}\int_A \omega(\xi)\left(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|\right)^2 \; dA_{\boldsymbol{\xi}} \\
    &=\frac{\beta}{2}\int_A  \omega(\xi) \frac{\epsilon_{ij}\xi_i \xi_j }{|\boldsymbol{\xi}|} \frac{\epsilon_{kl} \xi_k \xi_l }{|\boldsymbol{\xi}|}\;dA_{\boldsymbol{\xi}}\\
    &=\frac{\beta}{2} \epsilon_{ij}^d \epsilon_{kl}^d \int_A \frac{ \omega(\xi)}{|\boldsymbol{\xi}|^2}\xi_i \xi_j \xi_k \xi_l \;dA_{\boldsymbol{\xi}}\\
\end{align*}
%
With $i, j, k, l = 1,2$. For a circular $\omega$, combinations of $\{i,j,k,l\}$ with an odd number of any index, such as $\{1,1,1,2\}$ will integrate to 0.
%
\begin{align*}
%    m&=(\underline{\omega}\:\underline{x}) \bullet \underline{x}\\
    m &= \int_A \omega(\xi)|\boldsymbol{\xi}|^2\; dA_{\boldsymbol{\xi}} \\
    W^d_\text{PD} &= \frac{\beta \; m}{16}[3(\epsilon_{11}\epsilon_{11}+\epsilon_{22}\epsilon_{22})+(\epsilon_{11}\epsilon_{22}+\epsilon_{12}\epsilon_{12}+\epsilon_{12}\epsilon_{21}+\epsilon_{21}\epsilon_{12}+\epsilon_{21}\epsilon_{21}+\epsilon_{22}\epsilon_{11}]\\
    &= \frac{\beta \; m}{16} \epsilon_{ij}^d \epsilon_{kl}^d (\delta_{ij}\delta_{kl}+\delta_{ik}\delta_{jl}+\delta_{il}\delta_{jk})\\
    &= \frac{\beta \; m}{8} \epsilon_{ij}^d \epsilon_{ij}^d \implies\\
     \beta &= \frac{8 \; G\;h}{m}
\end{align*}
%

Having calibrated the bond-extension model to the shear modulus, applying a different uniform strain (such as might result from uniaxial tension) reveals the bond-based model to result in a one-parameter linearly-elastic model with Poisson's ratio \(\nu=\sfrac{1}{3}\).

Combining the bending and extension models allows for the description of more complex behaviors, particularly the stiffening effect of in-plane tension on the transverse bending of a plate.
Consider a single bond-pair in the combined model:
\begin{figure}
  \label{fig:hybridmodel}
  \centering
  \input{\diagrampath/bondPairCombinedV.tex}
  \caption{The Hybrid Model Combines Bending and Extension Components}
\end{figure}
As the two sides are pulled apart, the magnitude of the extension force in each bond increases, and the magnitude of the bending force decreases. 
At the same time, the angle at which the extension force acts decreases, and the angle of action for the bending force increases.
For small amounts of bending and reasonable stretches, increased tension in the direction of the bond pair results in increase restorative force.

\section{Extension to Arbitrary Poisson Ratio}
Although many materials have Poisson ratios of \(\nu\approx \sfrac{1}{3}\), it is nonetheless desirable to extend the model to materials with arbitrary Poisson ratios.
For isotropic, linearly elastic models of solid materials, Silling et. al. extended the peridynamic material model to arbitrary material parameters in \cite{silling2007peridynamic} by decomposing the deformation state into isotropic and deviatoric deformation states.
In the absence of plastic deformation, we need only find the difference between the strain energy of a deformed bond-based plate and the strain energy of an elastic plate with Poisson's ratio \(\nu \neq \sfrac{1}{3}\).
The difference is a function of the isotropic strain in two dimensions, \(\theta_2\)
%
\begin{align}
    W' &= \frac{G\;h}{2}\left(\frac{3\nu-1}{1-\nu}\right)\theta_2^2 \notag \\
%    \theta_2 &= \frac{2}{m}\left(\underline{\omega x}\right)\bullet\underline{e} \notag \\
    \theta_2 &= \frac{2}{m}\int_A \omega(\boldsymbol{\xi})|\boldsymbol{\xi}|(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|)\;dA_{\boldsymbol{\xi}} \notag \\
%    W_\text{total} &= \frac{G\;h}{2}\left(\frac{3\nu-1}{1-\nu}\right)\theta_2^2 + \frac{4\;G\;h}{m}\left(\underline{\omega e}\right)\bullet\underline{e}\notag
    W_\text{total} &= \frac{G\;h}{2}\left(\frac{3\nu-1}{1-\nu}\right)\theta_2^2 + \frac{4\;G\;h}{m}\int_A \omega(\boldsymbol{\xi})(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|)^2\;dA_{\boldsymbol{\xi}}\notag
\end{align}
%
This is to be expected because the bond-based model was calibrated to the shear strain energy, leaving discrepancies proportional to the isotropic strain energy that fall to 0 as Poisson's ratio approaches \(\nu = \sfrac{1}{3}\).

This decomposition method inspires a similar approach to the bending model
To perform the same extension for the plate model in bending, we find the error in the 1-parameter strain energy for \(\nu \neq \sfrac{1}{3}\)
%
\begin{align}
    W'=&\frac{G h^3}{12(1-\nu)} \left(\kappa_1^2+\kappa_2^2+2\nu\kappa_1\kappa_2+2(1-\nu)\kappa_3^2 \right)\notag\\
    &-\frac{G h^3}{12(1-\frac{1}{3})} \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\nu\kappa_1\kappa_2+2(1-\frac{1}{3})\kappa_3^2 \right) \notag \\
    W'=&2G \frac{h^3}{12}\frac{3\nu-1}{1-\nu} \left(\frac{\kappa_1+\kappa_2}{2}\right)^2.\notag
\end{align}
%
The discrepancy in energy is proportional to the square of average curvature, \(\frac{\kappa_1+\kappa_2}{2} = \bar{\kappa}\), which we will also refer to as the isotropic curvature.
The isotropic curvature can be envisioned as the portion of the deformation that resembles a spherical bowl.
A complete decomposition of bending energy into isotropic and deviatoric components as performed by Fischer in \cite{fischer1992bending} produces a far more complex model and is unnecessary at this time.
For a single bond pair we can represent the curvature vector along the bond pair as 
%\marginpar{ maybe leave this out and go straight to the curvature vector?}
%
\begin{equation}
    \boldsymbol{\kappa} _{\hat{\boldsymbol{\xi}}} = \frac{\vstate{Y}{}{\boldsymbol{\xi}}+\vstate{Y}{}{\boldsymbol{-\xi}}}{|\boldsymbol{\xi}|^2}\notag
\end{equation}
%
%\begin{equation}
%    \kappa_{\hat{u}} = \frac{z(\mathbf{x}+\xi\hat{u})-2z(\mathbf{x})+z(\mathbf{x}-\xi\hat{u})}{\xi^2}\notag
%\end{equation}
%
For large rotations, we can define an average curvature vector \(\bar{\boldsymbol{\kappa}}\).
This leads us to estimate the average curvature as 
%
\begin{align}
    \bar{\boldsymbol{\kappa}} &= \frac{1}{m_2} \int_0^\delta \int_0^{2\pi}\psi(\xi)\frac{\vstate{Y}{}{\boldsymbol{\xi}}+\vstate{Y}{}{\boldsymbol{-\xi}}}{\xi^2} \xi {\rm d}\phi {\rm d}\xi ;\notag \\
    m_2 &= \int_0^\delta \int_0^{2\pi}\psi(\xi)\xi {\rm d}\phi {\rm d}\xi. \notag
\end{align}
%
The weighting function \(\psi(\xi)\) performs a role similar to that of \(\omega(\xi)\) from the previous section, but need not be identical.
We can rewrite the energy discrepancy in terms of \(\bar{\boldsymbol{\kappa}}\).
%
\begin{equation}
    W'=2G\frac{h^3}{12}\frac{3\nu-1}{1-\nu}\frac{\bar{\boldsymbol{\kappa}}^2}{2}. \notag
\end{equation}
%
We can take the Fr\'{e}chet derivative to produce a correction force vector state
%
\begin{equation}
    \vstate{T'}{}{\boldsymbol{\xi}}=\frac{4G}{m_2}\frac{h^3}{12}\frac{3\nu-1}{1-\nu}\frac{\psi(\boldsymbol{\xi})}{\xi^2} \bar{\boldsymbol{\kappa}}\;dA,
    \label{eq:pressureState}
\end{equation}
%
that is not directly dependent on the deformation of a single bond pair.
Instead, \cref{eq:pressureState} represents a bond-length dependent ``pressure'' applied to every pair of bonds extending from a node.
This ``pressure'' is proportional to the curvature vector at that node.
A weighting function \(\psi(\boldsymbol{\xi}) = |\boldsymbol{\xi}|\) can ensure that the integral expression for force at a point is convergent.
This extra term that is dependent on the bending of all the pairs around a node means that the extension is not properly a \textit{bond-pair} model.
Instead, it would be more accurate to call it a \textit{bond-multiple} model, in which the bond forces and energies are functions of the relationship between a family of bonds.
In either the continuous or discrete cases, this model extension requires the additional step of evaluating the isotropic curvature at each point, but the increased complexity of the extended model captures in the local limit the behavior of a two-parameter elastic material plate.
%
\section{Numerical Simulation}
\subsection{Discretized Model}
Discretizing the bond-pair model is primarily matter of exchanging integrals for sums. 
%
\begin{align}
%\label{eq:discreteBeamw}
w(\boldsymbol{\xi}_i) &= \omega(\boldsymbol{\xi}_i)\alpha \left[1+\cos(\theta(\vstate{Y}{}{\boldsymbol{\xi}_i},\vstate{Y}{}{-\boldsymbol{\xi}_i})) \right] \notag \\
&\approx \omega(\boldsymbol{\xi}_i)\frac{\alpha}{2}\left(\frac{z(\mathbf{x}+\boldsymbol{\xi}_i)-2z(\mathbf{x})+z(\mathbf{x}-\boldsymbol{\xi}_i)}{\boldsymbol{\xi}_i}\right)^2 \notag
\end{align}
%
in which $\boldsymbol{\xi}_i$ is the $i^\textnormal{th}$ bond emanating from the point $\mathbf{x}$ to each of the $n$ points within distance $\delta$ of point $\mathbf{x}$.
%
\begin{align}
    \label{eq:discretebeam}
    \alpha &= \frac{c\; (\Delta x)^2}{m} ;\; c= \frac{G}{(1-\nu)}\frac{h^3}{12};\; m=\sum_{i=1}^n \omega(\boldsymbol{\xi}_i)\boldsymbol{\xi}_i^2 \implies \nonumber \\
    W&=(\Delta x)^2 \sum_{i=1}^n \omega(\boldsymbol{\xi}_i)\frac{G}{2(1-\nu)}\frac{h^3}{12}\left(\frac{z(\mathbf{x}+\boldsymbol{\xi}_i)-2z(\mathbf{x})+z(\mathbf{x}-\boldsymbol{\xi}_i)}{|\boldsymbol{\xi}_i|}\right)^2 \notag
\end{align}
%
Discretization of the 1-parameter bending model results in the equation of motion
%
\begin{align}
    \rho(\mathbf{x})\mathbf{\ddot{u}}(\mathbf{x}) = \mathbf{f}(\mathbf{x})&+\sum_i \omega(\boldsymbol{\xi}_i)\left\{\frac{\alpha(\mathbf{x})}{|\mathbf{p}_i |}\frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \left[ \frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \frac{\mathbf{q}_i}{|\mathbf{q}_i |}\right] \right. \notag \\
    & \left. -\frac{\alpha(\mathbf{x}+\boldsymbol{\xi}_i)}{|\mathbf{p}_i |}\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times\left[\frac{(-\mathbf{p}_i)}{|\mathbf{p}_i |}\times \frac{\mathbf{r}_i}{|\mathbf{r}_i |} \right] \right\} \notag
\end{align}
with
\begin{align}
    \mathbf{p}_i &= \boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}+\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x});\notag\\
    \mathbf{q}_i &= -\boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}-\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x});\notag\\
    \mathbf{r}_i &= \boldsymbol{\xi}_i+\mathbf{u}(\mathbf{x}+2\boldsymbol{\xi}_i)-\mathbf{u}(\mathbf{x}+\boldsymbol{\xi}_i).\notag
\end{align}
%

Implementing the 2-parameter model requires finding the isotropic curvature at each point.
%
\begin{align*}
    \bar{\boldsymbol{\kappa}}(\mathbf{x}) &= \frac{1}{m_2} \sum_i \psi(\boldsymbol{\xi}_i)\frac{\mathbf{p}_i +\mathbf{q}_i }{\boldsymbol{\xi}_i^2};\notag \\
    m_2(\mathbf{x})  &= \sum_i \psi(\boldsymbol{\xi}_i); \notag \\
    \alpha^\text{iso}(\mathbf{x}) &= \frac{4G}{m_2}\frac{h^3}{12}\frac{3\nu-1}{1-\nu}(\Delta x)^2;\\
    f^\text{iso}(\mathbf{x}) &= \sum_j \left\{\left[\alpha^\text{iso}(\mathbf{x})\bar{\boldsymbol{\kappa}}(\mathbf{x})-\alpha^\text{iso}(\mathbf{x}+\boldsymbol{\xi}_j)\bar{\boldsymbol{\kappa}}(\mathbf{x}+\boldsymbol{\xi}_j) \right] \frac{\omega(\boldsymbol{\xi}_j)}{\boldsymbol{\xi}_j^2} \right\}
\end{align*}
%
Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced throughout the entire plate, otherwise the displacement \(z(\mathbf{x}-\boldsymbol{\xi}_i)\) is ill-defined. 
For this reason, the discretization does not allow for areas of higher and lower ``resolution''. 
%
\subsection{Numerical Method}
\label{sec:NumMethod}
Model behavior is evaluated by implementing the discretized equation of motion.
The case of a square plate simply supported on all four sides is chosen for simplicity in both evaluation and comparison.
To implement the simply-supported condition, it was sufficient to constrain the vertical displacement of each node along the plate's four edges.
Boundary conditions such as clamped or guided supports and applied moments require careful treatment to ensure both meaningful results and ease of computation.
While applying displacement constraints is straightforward, the appropriate way to apply an angle constraint or moment to a peridynamic point or collection of points is less obvious.

Additionally, the simply-supported flat plate is a configuration with significant analytical treatment, making a better comparison case than configurations that may require comparison to finite element or other solution techniques.
%
\subsection{Results}
The simplest test case for this model is a linear-elastic square plate with Poisson's ratio \(\nu = \sfrac{1}{3}\) that is simply-supported on all 4 sides with a uniform transverse pressure load on the entire surface between the supports.
As expected from an energy-equivalent model, the slice along the plate's centerline shown in \cref{fig:elastic_plate} demonstrates good agreement between the static deflection predicted by the bond-pair model and that of classical linear elasticity.
Accurate results require a denser discretization than is the case for the elastic beams from previous work.

%
\begin{figure}[h]
  \centering
  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_convergence_n.pgf}}
  \caption{The Bond-Pair Model Converges on Accurate Plate Deflection}
  \label{fig:elastic_plate}
\end{figure}

The test case for the hybrid model is a similar simply-supported square plate with an additional in-plane tension load along two opposing sides.
An analytical solution for this combination of uniform transverse pressure and in-plane edge tension can be found in Timoshenko's book~\cite{timoshenko1959theory}.
As is mechanically intuitive, increasing in-plane tension results in decreasing transverse displacement, while the opposite is true for compressive edge loading.
Normalized to the the maximum displacement of a transversely-loaded plate with no in-plane edge loads, the results in \cref{fig:plateStiffening} show that the hybrid model does a good job of simulating the impact of in-plane tension on maximum transverse deflection.

\begin{figure}[h]
  \centering
  \resizebox{0.55\linewidth}{!}{\input{\plotpath/plateStiffening.pgf}}
  \caption{The Combined Model Accurately Captures the Influence of In-Plane Tension}
  \label{fig:plateStiffening}
\end{figure}

The bond-multiple plate model is motivated by the desire to extend the bending model to an arbitrary Poisson's ratio, so the obvious test for this model is the same as for the bond-pair model. When compared to analytical predictions, \cref{fig:plate_poisson} demonstrates the bond-multiple model's ability to simulate plates with Poisson's ratios that depart significantly from the bond-pair limitation of $\nu = \sfrac{1}{3}$.

\begin{figure}[h]
  \centering
  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlatePoissonEffect.pgf}}
  \caption{The Extended Model Matches for Arbitrary Poisson's Ratio}
  \label{fig:plate_poisson}
\end{figure}

\section{Conclusion}

The non-ordinary bond-pair model is the first peridynamic material model to directly resist bending deformation.
Previously introduced as a beam bending model, a simple extension to two dimensions is demonstrated to accurately simulate a simple Kirckhoff-Love plate example.
When combined with a simple bond-stretch model, the hybrid model successfully reproduces the shell-stiffening behavior expected of a plate resisting combined in-plane and transverse loads.
Calculating isotropic bending and extension states allows for a straightforward extension of both models to account for isotropic deformation energy and enables accurate modeling of plates with arbitrary Poisson's ratios.

\appendix
\section{Fr\'echet Derivative}
\label{sec:frechet}

The derivative of a function of a state is defined by Silling in \cite{silling2007peridynamic} as follows:
\begin{quote}
Let $\Psi$ be a function of a state, $\Psi(\cdot):\mathcal{A}_m\rightarrow\mathcal{L}_n$. Suppose there exists a state-valued function denoted $\nabla\Psi\in\mathcal{A}_{m+n}$ such that for any $\vstate{A}{}{}\in\mathcal{A}_m$ and any $\Delta\vstate{A}{}{}\in\mathcal{A}_m$,
\begin{equation}
  \Psi(\vstate{A}{}{}+\Delta\vstate{A}{}{})=\Psi(\vstate{A}{}{})+\nabla\Psi(\vstate{A}{}{})\bullet\Delta\vstate{A}{}{}+o(||\Delta\vstate{A}{}{}||).
\end{equation}
Then $\Psi$ is said to be \textit{differentiable} and $\nabla\Psi$ is called the \textit{Frechet derivative} of $\Psi$.
\end{quote}
This is a fairly straightforward way of defining a derivative with respect to a state, and we will apply it to derive the bond force function from the bond-pair energy function
%
\begin{align}
%
\tvstate{T}{}{\boldsymbol{\xi}} &= \nabla w\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}\right)\notag \\
%
w&=\omega\!\left(\boldsymbol{\xi}\right)\alpha\left[1+\cos\!\left(\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right)\right]\notag \\
%
w\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}+\Delta\tvstate{Y}{}{\boldsymbol{\xi}}\right) &=
 \omega\!\left(\boldsymbol{\xi}\right)\alpha\left[1+\cos\!\left(\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}+\Delta\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right)\right]\notag
\end{align}
%
\begin{multline}
\nabla w\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}\right)\bullet\Delta\tvstate{Y}{}{\boldsymbol{\xi}}= 
w\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}+\Delta\tvstate{Y}{}{\boldsymbol{\xi}}\right) -w\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}\right) \notag\\
%
=\omega\!\left(\boldsymbol{\xi}\right)\alpha\sin\!\left(\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right)\!\left[\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}+\Delta\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)-\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right]
\end{multline}
%
\begin{equation}
\left[\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}}+\Delta\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)-\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right] = 
\frac{\Delta\tvstate{Y}{}{\boldsymbol{\xi}}}{|\tvstate{Y}{}{\boldsymbol{\xi}}|}\bullet \hat{\theta}\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\notag
\end{equation}
%
To determine the $\hat{\theta}$ direction vector, we must construct a vector that is normal to $\tvstate{Y}{}{\boldsymbol{\xi}}$ and that is in the plane containing both $\vstate{Y}{}{\boldsymbol{\xi}}$ and $\vstate{Y}{}{\boldsymbol{-\xi}}$.
The cross product of $\vstate{Y}{}{\boldsymbol{\xi}}$ and $\vstate{Y}{}{\boldsymbol{-\xi}}$ is a vector normal to that plane, so any vector normal to that cross product will be in the correct plane.
Therefore, the vector $\vstate{Y}{}{\boldsymbol{\xi}}\times\left[\vstate{Y}{}{\boldsymbol{\xi}}\times\vstate{Y}{}{\boldsymbol{-\xi}}\right]$ is both normal to $\vstate{Y}{}{\boldsymbol{\xi}}$ and is in the plane containing both $\vstate{Y}{}{\boldsymbol{\xi}}$ and $\vstate{Y}{}{\boldsymbol{-\xi}}$.
Normalizing gives us the $\hat{\theta}$ direction vector:
%
\begin{equation}
\hat{\theta}\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)=
\frac{\tvstate{Y}{}{\boldsymbol{\xi}}\times\left[\tvstate{Y}{}{\boldsymbol{\xi}}\times\tvstate{Y}{}{\boldsymbol{-\xi}}\right]}{|\tvstate{Y}{}{\boldsymbol{\xi}}||\tvstate{Y}{}{\boldsymbol{\xi}}||\tvstate{Y}{}{\boldsymbol{-\xi}}|\sin\!\left(\theta\!\left(\tvstate{Y}{}{\boldsymbol{\xi}},\tvstate{Y}{}{-\boldsymbol{\xi}}\right)\right)}\notag 
\end{equation}
%
We combine all of these to get the expression for bond force found in \cref{eq:SillingForceNO}.
\begin{align}
%
\tvstate{T}{}{\boldsymbol{\xi}} &=
\omega\!\left(\boldsymbol{\xi}\right)\frac{-\alpha}{|\tvstate{Y}{}{\boldsymbol{\xi}}|} \frac{\tvstate{Y}{}{\boldsymbol{\xi}}}{|\tvstate{Y}{}{\boldsymbol{\xi}}|} \times 
\left[\frac{\tvstate{Y}{}{\boldsymbol{\xi}}}{|\tvstate{Y}{}{\boldsymbol{\xi}}|} \times 
\frac{\tvstate{Y}{}{-\boldsymbol{\xi}}}{|\tvstate{Y}{}{-\boldsymbol{\xi}}|}\right]\notag
\end{align}
%

\bibliographystyle{elsarticle-num}
\bibliography{jogrady_bibdesk}

\end{document} 
\end

### 2014-04-24 diagrams/bondPair.tex
initial draft commit

\begin{tikzpicture}[y=0.80pt, x=0.8pt,yscale=-1, inner sep=0pt, outer sep=0pt]
\begin{scope}[shift={(-71.10332,-65.91978)}]
  \path[draw=black,dash pattern=on 1.60pt off 0.80pt,line join=miter,line
    cap=butt,miter limit=4.00,line width=0.800pt] (100.0000,102.3622) --
    (200.0000,102.3622) -- (300.0000,102.3622);
  \path[draw=black,line join=miter,line cap=butt,line width=0.800pt]
    (72.0000,92.3622) -- (75.0000,77.3622) -- (200.0000,102.3622) --
    (300.0000,77.3622) -- (305.0000,97.3622);
  \path[draw=black,line join=miter,line cap=butt,line width=0.800pt]
    (75.0000,77.3622) -- (200.0000,102.3622) -- (300.0000,77.3622);
  \path[draw=black,line join=miter,line cap=butt,line width=0.800pt]
    (200.0000,102.3622) -- (198.0000,67.3622);
  \path[fill=black] (178.797,148.02312) node[above right] (text6246) {};
  \path[fill=black] (276.10333,95.203163) node[above right] (text6273)
    {$\mathbf{\xi}$};
  \path[fill=black] (106.10332,125.20316) node[above right] (text6277)
    {$\mathbf{\xi}$};
  \path[fill=black] (146.10332,75.203163) node[above right] (text6281)
    {$\vstate{Y}{}{\mathbf{-\xi}}$};
  \path[fill=black] (256.10333,80.203163) node[above right] (text6285)
    {$\vstate{Y}{}{\mathbf{\xi}}$};
\end{scope}

\end{tikzpicture}

### 2014-04-25 PlatePaper.tex
Small edits and corrections

@@
 \usepackage[section]{placeins}
+\usepackage[color=red!40, textsize=scriptsize]{todonotes}
 
@@
 This model is non-ordinary and derived from the concept of a rotational spring between bonds.
-A simple extension of the beam model reproduces plate bending with a poisson ratio of \(\nu=\sfrac{1}{3}\), which can be combined with a 2D linear peridynamic solid model to simulate mixed in-plane and transverse loading.
-The addition of an isotropic bending state term extends the model to arbitrary poisson ratios.
+A simple extension of the beam model reproduces plate bending with a Poisson ratio of \(\nu=\sfrac{1}{3}\), which can be combined with a 2D linear peridynamic solid model to simulate mixed in-plane and transverse loading.
+The addition of an isotropic bending state term extends the model to arbitrary Poisson ratios.
 Simple test cases demonstrate the model's performance.
@@
 \section{Introduction}
-A goal of many mechanical engineering analyses is the prediction and description of material failure.
+\todo{Lets not start this paper with the exact same paragraph as the last paper.} A goal of many mechanical engineering analyses is the prediction and description of material failure.
 When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.
@@
 This paper extends the author's previous work on 1D beams to model the bending of a flat Kirckhoff-Love plate.
-The resulting 1-parameter model is constrained to a poisson ratio \(\nu=\sfrac{1}{3}\).
-The model is combined with an extension-based model to capture the impact of in-plane forces on bending behavior.
-By introducing an isotropic bending state, the model is extended to any valid poisson ratio.
+The resulting 1-parameter model is constrained to a Poisson ratio \(\nu=\sfrac{1}{3}\).
+The model is combined with an extension-based model to capture the effect of in-plane forces on bending behavior.
+By introducing an \emph{isotropic bending-state}, the model is extended to any valid Poisson ratio.
 In addition to directly modeling a thin flat plate in bending, the simple plate case lays the theoretical framework for more complex peridynamic plate and shell bending models.
@@
 
-The second section of this paper provides a brief introduction to peridynamics, including state based models.
-The third section presents the state based plate model and demonstrates equivalence to 1-parameter classical Kirckhoff-Love plate theory in the limit of shrinking nonlocality.
+The second section of this paper provides a brief introduction to peridynamics, including state-based models.
+The third section presents the state based plate model and demonstrates equivalence to 1-parameter classical Kirckhoff-Love plate theory in the limit of vanishing nonlocality.
 Also in the third section, the bending model is combined with an extension-based model to resist both in-plane and out-of-plane deformations.
-The fourth section introduces the isotropic bending state and extends the plate to arbitrary poisson ratios.
+The fourth section introduces the isotropic bending-state and extends the plate to arbitrary Poisson ratios.
 The fifth section demonstrates the model with simple test cases.
+
 %
@@
 \label{sec:PDintro}
-The term \textit{peridynamic} alludes to the fact that the force at a point is affected by nearby material configuration and was coined by Silling to describe the new formulation of continuum mechanics he developed in \cite{silling2000reformulation}.
+\todo{Again, not word-for-word} The term \textit{peridynamic} alludes to the fact that the force at a point is affected by nearby material configuration and was coined by Silling to describe the new formulation of continuum mechanics he originally developed in \cite{silling2000reformulation}.
 Weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.
-These higher-order derivatives impose stronger continuity requirements than the classical model. 
+These higher-order derivatives impose stronger continuity requirements than the classical models.
 By contrast, the peridynamic model is strongly nonlocal and casts material behavior at a point as the \textit{integral} equation
@@
     \label{eq:PDCoPV}
-    \rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega \mathbi{f}(\mathbf{x},\mathbf{q}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}) \notag
+    \rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega \mathbi{f}(\mathbf{x},\mathbf{q}) {\rm d}V_\mathbf{q}  + \mathbf{b}(\mathbf{x}) \notag
 \end{equation}
@@
 rather than the classical \textit{partial-differential equation}.
-Instead of the divergence of stress, we have the integral of a ``force" function $\mathbi{f}$ of the position vector $\mathbf{x}$ and the position vector $\mathbf{q}$ of a point within the body domain $\Omega$.
+Instead of the divergence of stress, we have the integral of a ``force'' functional $\mathbi{f}$ of the position vector $\mathbf{x}$ and the position vector $\mathbf{q}$ of a point within the body domain $\Omega$.
 This force functional may depend on \(\mathbf{x}\), \(\mathbf{q}\), their deformed positions, the original and deformed positions of other points in \(\Omega\), history, etc.
@@
 Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.
-While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic}.
+While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic, silling2007peridynamic, foster2010viscoplasticity}\todo{Cite several more papers here, including your forthcoming beam paper}.
 
-To describe force functionals that incorporate the behavior of a totality of points in the nearby material (not just $\mathbf{x}$ and $\mathbf{q}$), we must introduce the concept of a peridynamic state.
+To describe force functionals that incorporate the behavior of a totality of points in the nearby material (not just $\mathbf{x}$ and $\mathbf{q}$), we must introduce the concept of a peridynamic \emph{state}.
 
-Introduced by Silling et al.\ in 2007~\cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.
-The most common states are scalar-states and vector-states which are scalar and vector valued, respectively.
+Introduced by Silling et al.\ \cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.
+The most common states are \emph{scalar-states} and \emph{vector-states} which are scalar and vector valued, respectively.
+
 Unlike a second order tensor, which can only map vectors linearly to other vectors, vector-states can produce nonlinear or even discontinuous mappings.
@@
 Models in which they are not in the same direction are called \textit{non-ordinary}.
-Silling et al. demonstrate the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.
-Foster et al.
-\cite{foster2010viscoplasticity} and Warren et.
-al.
-\cite{warren2009non} show that correspondence models, which approximate the deformation gradient and use it to calculate bond forces, result in non-ordinary state based constitutive models for deformation with large rotation.
+Silling et al.\ discussed the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.
+Foster et al.\ \cite{foster2010viscoplasticity} and Warren et al.\ \cite{warren2009non} showed that correspondence models, which approximate a deformation gradient and use it to calculate bond forces based on classical constitutive models, result in non-ordinary state based constitutive models for finite deformations.
 %

### 2014-04-25 PlatePaper.tex
addressed comments on intro and peridynamics sections

@@
 \section{Introduction}
-\todo{Lets not start this paper with the exact same paragraph as the last paper.} A goal of many mechanical engineering analyses is the prediction and description of material failure.
+%\todo{Lets not start this paper with the exact same paragraph as the last paper.} A goal of many mechanical engineering analyses is the prediction and description of material failure.
 When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.
@@
 The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
+The peridynamic formulation of continuum mechanics defines material behavior at a point as an integral function of the behavior of nearby points.
+By doing so, it eliminates the need to calculate gradients of displacement (required in classical continuum mechanics) and the accompanying continuity requirements.
+This is particularly valuable when examining material failure, in which discontinuous displacements feature heavily.
+Because predicting and modeling material failure is a primary goal of many analyses, peridynamic material models have attracted significant interest, resulting in several 3D solid material models \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}.
+Similar models have been used to capture tension and compression in 1D bars\cite{silling2003deformation} and 2D membranes\cite{silling2005peridynamic}, but using them to model bending behavior requires a discretization with several nodes through the thickness of the feature, resulting in very computationally expensive models.
+A recent paper by Taylor and Steigmann \cite{taylor2013two} approaches this problem by reducing a bond based 3D plate to two dimensions with an integral through the plate's thickness.
+This creates a model that can represent thin structures with courser discretization.
+Although Taylor and Steigmann's model includes a bending term, it is demonstrated only for in-plane loading.
+The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
+
+\todo{figure out where to put this} Outside of peridynamics, weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.
 A nonlocal plate model by Ansari et al.
-\cite{ansari2010nonlocal} applies Eringen elasticity to Mindlin plate theory, an approach which captures scale effects but imposes stricter continuity requirements.
+\cite{ansari2010nonlocal} applies Eringen elasticity to Mindlin plate theory, an approach which captures scale effects but imposes even stricter continuity requirements than the classical formulation.
 
@@
 \label{sec:PDintro}
-\todo{Again, not word-for-word} The term \textit{peridynamic} alludes to the fact that the force at a point is affected by nearby material configuration and was coined by Silling to describe the new formulation of continuum mechanics he originally developed in \cite{silling2000reformulation}.
-Weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.
-These higher-order derivatives impose stronger continuity requirements than the classical models.
+%\todo{Again, not word-for-word} The term \textit{peridynamic} alludes to the fact that the force at a point is affected by nearby material configuration and was coined by Silling to describe the new formulation of continuum mechanics he originally developed in \cite{silling2000reformulation}.
 By contrast, the peridynamic model is strongly nonlocal and casts material behavior at a point as the \textit{integral} equation
+Stuart Silling first developed the theory of peridynamics in~\cite{silling2000reformulation} to eliminate the problems associated with the undefined partial derivatives that attend the formation of cracks.
+The name refers to the force exerted on a point by material points a finite distance away.
+As a strongly nonlocal model, peridynamics casts material behavior at a point as the \textit{integral} equation
 %
@@
 Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.
-While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic, silling2007peridynamic, foster2010viscoplasticity}\todo{Cite several more papers here, including your forthcoming beam paper}.
+While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and many other behaviors \cite{silling2005peridynamic, dayal2006kinetics, gerstle2007peridynamic, silling2007peridynamic, warren2009non, foster2010viscoplasticity,foster2011energy,taylor2013two,ogrady2014beams}\todo{Cite several more papers here}.
 
 To describe force functionals that incorporate the behavior of a totality of points in the nearby material (not just $\mathbf{x}$ and $\mathbf{q}$), we must introduce the concept of a peridynamic \emph{state}.
-
 Introduced by Silling et al.\ \cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.
@@
 Models in which they are not in the same direction are called \textit{non-ordinary}.
-Silling et al.\ discussed the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.
+Silling et al.\ discussed the possibility of such models in \cite{silling2010peridynamic}, but little work has touched on their use.
 Foster et al.\ \cite{foster2010viscoplasticity} and Warren et al.\ \cite{warren2009non} showed that correspondence models, which approximate a deformation gradient and use it to calculate bond forces based on classical constitutive models, result in non-ordinary state based constitutive models for finite deformations.
+Recent work by O'Grady and Foster \cite{ogrady2014beams} uses a non-ordinary material model to simulate bending in 1D beams.
 %

### 2014-04-28 PlatePaper.tex
added h-convergence and minimum horizon plots

@@
 The simplest test case for this model is a linear-elastic square plate with Poisson's ratio \(\nu = \sfrac{1}{3}\) that is simply-supported on all 4 sides with a uniform transverse pressure load on the entire surface between the supports.
-As expected from an energy-equivalent model, the slice along the plate's centerline shown in \cref{fig:elastic_plate} demonstrates good agreement between the static deflection predicted by the bond-pair model and that of classical linear elasticity.
+As expected from an energy-equivalent model, the slice along the plate's centerline shown in \cref{fig:plate_convergence_h} demonstrates good agreement between the static deflection predicted by the bond-pair model and that of classical linear elasticity as the horizon length shrinks.
+The minimum horizon size depends on the discretization; it appears that twice the node spacing is insufficient, and that three times the node spacing is sufficient.
+The difference is evident in \cref{fig:plate_minimum_h}.
+
+%
+\begin{figure}[h]
+  \centering
+  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_convergence_h.pgf}}
+  \caption{The Bond-Pair Model Converges on Accurate Plate Deflection with Smaller Horizons}
+  \label{fig:plate_convergence_h}
+\end{figure}
+
+%
+\begin{figure}[h]
+  \centering
+  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_minimum_h.pgf}}
+  \caption{Horizon Must Include Sufficient Nodes}
+  \label{fig:plate_minimum_h}
+\end{figure}
+
 Accurate results require a denser discretization than is the case for the elastic beams from previous work.
+\Cref{fig:plate_convergence_n} illustrates the model converging to the analytical solution as the discretization is made finer.
 
@@
   \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_convergence_n.pgf}}
-  \caption{The Bond-Pair Model Converges on Accurate Plate Deflection}
-  \label{fig:elastic_plate}
+  \caption{The Bond-Pair Model Converges on Accurate Plate Deflection with Finer Dsicretization}
+  \label{fig:plate_convergence_n}
 \end{figure}

### 2014-04-30 PlatePaper.tex
minor edits to results section
More small edits

--- 2014-04-25 PlatePaper.tex
@@
 \usepackage[section]{placeins}
-\usepackage[color=red!40, textsize=scriptsize]{todonotes}
+\usepackage[color=red!40, textsize=scriptsize, textwidth=1.0in]{todonotes}
 
@@
 \section{Introduction}
-\todo{Lets not start this paper with the exact same paragraph as the last paper.} A goal of many mechanical engineering analyses is the prediction and description of material failure.
+\todo{Lets not start this paper with the exact same sentence as the last paper.} A goal of many mechanical engineering analyses is the prediction and description of material failure.
 When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.
@@
 Various peridynamic material models capture the deformation behavior of 3-dimensional solid objects \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}, but would be very expensive to implement for a thin plate or beam, as the thru-thickness discretization requirement to properly capture resistance to bending would be prohibitively expensive in a computational setting for a long, slender structural object.
-Other peridynamic models capture tension and compression in 1D bars\cite{silling2003deformation} and 2D membranes\cite{silling2005peridynamic}, but these features do not resist transverse displacement.
+Other peridynamic models capture tension and compression in 1D bars \cite{silling2003deformation} and 2D membranes \cite{silling2005peridynamic}, but these features do not resist transverse displacement.
 A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness.
@@
 Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.
-While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic, silling2007peridynamic, foster2010viscoplasticity}\todo{Cite several more papers here, including your forthcoming beam paper}.
+While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic, silling2007peridynamic, foster2010viscoplasticity, foster2011energy, jogrady2014a}\todo{Cite several more papers here.}.
 
@@
 
-Just as stress and strain are work conjugate, so too are the force and deformation vector states for hyperelastic materials.
+Just as stress and strain are work conjugate, so too are the force and deformation vector-states for hyperelastic materials.
 If the force state $\vstate{T}{}{}$ is always in the same direction as the deformation state $\vstate{Y}{}{}$, then the force exerted by a ``bond'' between points is in the same direction as the deformed bond, and the model is called \textit{ordinary}.
@@
 %
-\begin{figure}[h]
+\begin{figure}[tbp]
     \centering
     \subinputfrom{\diagrampath/}{simpleBondPair.eps_tex}
-    \caption{Illustration of a bond pair model that resists angular deformation}
+    \caption{Illustration of a bond pair model that resists angular deformation.}
     \label{fig:SimpleBondpair}
@@
 %
-If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} by taking the Fr\'echet derivative.
+If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \todo{Need to define $\boldsymbol{\xi}$ somewhere} \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} and analyzed in \cite{jogrady2014a} by taking the Fr\'echet derivative.
 For the derivation and a description of the Fr\'echet derivative see \ref{sec:frechet}.
@@
 %
-\begin{figure}[h]
+\begin{figure}[tbp]
     \centering
     \subinputfrom{\diagrampath/}{continuousPlate.eps_tex}
-    \caption{Illustration of a bond pair on a plate}
+    \caption{Illustration of a bond pair on a plate.}
     \label{fig:BondPairPlate}
@@
 %
-\begin{figure}[h]
+\begin{figure}[tbp]
     \centering
@@
 This response is consistent with the idea of a rotational spring between bonds as long as the change in angle is small.
-Because the potential energy and force states are functions of \textit{pairs} of peridynamic bonds, we will call this formulation a \textit{bond-pair model}. 
+Because the potential energy and force-states are functions of \textit{pairs} of peridynamic bonds, we will call this formulation a \textit{bond-pair model}.
 Other choices for the bond-pair potential function, such as \( w = (\pi - \theta)^2 \), are also possible, but result in more mathematically complex analysis.
+
 \subsection{Energy Equivalence}
@@
 when the nonlocal length scale vanishes.
-We will begin with the assumptions from Kirckhoff plate theory: straight lines normal to the mid-surface remain both straight and normal to the deformed mid-surface, and plate thickness that does not change with deformation.
+We will begin with the assumptions from Kirckhoff plate theory: straight lines normal to the mid-surface remain both straight and normal to the deformed mid-surface, and the plate thickness does not change with deformation.
 While we will start with the original assumptions from Kirchoff-Love plate theory of small displacements and rotations, they will not constrain the validity of the model for larger displacements and rotations.
@@
 \end{align}
+\todo{It's a little unclear how $m$ arrises below from this equation.  Please see if you can make it more clear.} 
 %
@@
 
-It must be noted that the restriction \(\nu=\sfrac{1}{3}\) is the same imposed by the use of a bond based peridynamic model for in-plane deformation of a 2D peridynamic plate.
+It should be noted that the restriction \(\nu=\sfrac{1}{3}\) is the same imposed by the use of a bond based peridynamic model for in-plane deformation of a 2D peridynamic plate.
 
 \subsection{Combining Bending and Extension Models}
-The bond-pair bending model does not resist deformations that preserve the angles between opposite bonds, such as in-plane stretch or shear.
+The bond-pair bending model does not resist deformations that preserve the angles between opposite bonds\todo{This reads a little funny, could we not say: \ldots resist in-plane stretching or shear deformation.}, such as in-plane stretch or shear \todo{or you might just say: \dots does not develop membrane forces.}.
 If these behaviors are expected in combination with bending, a useful model must resist both.
-To create a plate model that also resists these deformations, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from \cite{silling2000reformulation}.
+To create a plate model that also resists these deformations, i.e.\ a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from \cite{silling2000reformulation}.
 In this model, individual bonds act as springs resisting changes in length.
@@
 By matching the energy of a plate in shear deformation, we can relate \(\beta\) to the shear modulus and thickness of the plate.
-Following the example of \cite{silling2007peridynamic}, we begin with a plate under pure in-plane shear.
+Following the example of \cite{silling2007peridynamic}, we begin with a plate \todo{should this be shell?} under pure in-plane shear.
 In Einstein notation, the strain energy of this plate is
@@
 \begin{align*}
-    W_\text{C} &= G \; h \; \epsilon_{ij}^d \epsilon_{ij}^d \\
-    W_\text{PD} &= \frac{\beta}{2}\int_A \omega(\xi)\left(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|\right)^2 \; dA_{\boldsymbol{\xi}} \\
-    &=\frac{\beta}{2}\int_A  \omega(\xi) \frac{\epsilon_{ij}\xi_i \xi_j }{|\boldsymbol{\xi}|} \frac{\epsilon_{kl} \xi_k \xi_l }{|\boldsymbol{\xi}|}\;dA_{\boldsymbol{\xi}}\\
-    &=\frac{\beta}{2} \epsilon_{ij}^d \epsilon_{kl}^d \int_A \frac{ \omega(\xi)}{|\boldsymbol{\xi}|^2}\xi_i \xi_j \xi_k \xi_l \;dA_{\boldsymbol{\xi}}\\
+    W_\text{C} &= G \; h \; \epsilon_{ij}^d \epsilon_{ij}^d,  \\  \\
+    W_\text{PD} &= \frac{\beta}{2}\int_A \omega(\xi)\left(|\vstate{Y}{}{\boldsymbol{\xi}}|-|\boldsymbol{\xi}|\right)^2 \; {\rm d}A_{\boldsymbol{\xi}}, \\
+    &=\frac{\beta}{2}\int_A  \omega(\xi) \frac{\epsilon_{ij}\xi_i \xi_j }{|\boldsymbol{\xi}|} \frac{\epsilon_{kl} \xi_k \xi_l }{|\boldsymbol{\xi}|}\;{\rm d}A_{\boldsymbol{\xi}},\\
+    &=\frac{\beta}{2} \epsilon_{ij}^d \epsilon_{kl}^d \int_A \frac{ \omega(\xi)}{|\boldsymbol{\xi}|^2}\xi_i \xi_j \xi_k \xi_l \;{\rm d}A_{\boldsymbol{\xi}}.
 \end{align*}
@@
 %
-
 Having calibrated the bond-extension model to the shear modulus, applying a different uniform strain (such as might result from uniaxial tension) reveals the bond-based model to result in a one-parameter linearly-elastic model with Poisson's ratio \(\nu=\sfrac{1}{3}\).
@@
 Consider a single bond-pair in the combined model:
-\begin{figure}
+%
+\begin{figure}[tbp]
   \label{fig:hybridmodel}
@@
 \end{figure}
+%
 As the two sides are pulled apart, the magnitude of the extension force in each bond increases, and the magnitude of the bending force decreases.
@@
 
-\section{Extension to Arbitrary Poisson Ratio}
+\section{Extension to arbitrary Poisson ratio}
 Although many materials have Poisson ratios of \(\nu\approx \sfrac{1}{3}\), it is nonetheless desirable to extend the model to materials with arbitrary Poisson ratios.
-For isotropic, linearly elastic models of solid materials, Silling et.
-al.
-extended the peridynamic material model to arbitrary material parameters in \cite{silling2007peridynamic} by decomposing the deformation state into isotropic and deviatoric deformation states.
+For isotropic, linearly elastic models of solid materials, Silling et al.\ extended the peridynamic material model to arbitrary material parameters in \cite{silling2007peridynamic} by decomposing the deformation into isotropic and deviatoric components.
 In the absence of plastic deformation, we need only find the difference between the strain energy of a deformed bond-based plate and the strain energy of an elastic plate with Poisson's ratio \(\nu \neq \sfrac{1}{3}\).
@@
 
-This decomposition method inspires a similar approach to the bending model
+This decomposition method inspires a similar approach to our plate model.
 To perform the same extension for the plate model in bending, we find the error in the 1-parameter strain energy for \(\nu \neq \sfrac{1}{3}\)
@@
 %
-\begin{figure}[h]
+\begin{figure}[tbp]
   \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[tbp]
   \centering

### 2014-05-05 PlatePaper.tex
added double-torsion test

@@
 \section{Introduction}
-\todo{Lets not start this paper with the exact same sentence as the last paper.} A goal of many mechanical engineering analyses is the prediction and description of material failure.
+Modeling material failure is one of the most common challenges in mechanical engineering analysis.
 When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.
@@
 The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
+Outside of peridynamics, weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.
 A nonlocal plate model by Ansari et al.
-\cite{ansari2010nonlocal} applies Eringen elasticity to Mindlin plate theory, an approach which captures scale effects but imposes stricter continuity requirements.
+\cite{ansari2010nonlocal} applies Eringen elasticity to Mindlin plate theory, an approach which captures scale effects but imposes even stricter continuity requirements than the classical formulation.
+
+The peridynamic formulation of continuum mechanics defines material behavior at a point as an integral function of the behavior of nearby points.
+By doing so, it eliminates the need to calculate gradients of displacement (required in classical continuum mechanics) and the accompanying continuity requirements.
+This is particularly valuable when examining material failure, in which discontinuous displacements feature heavily.
+Because predicting and modeling material failure is a primary goal of many analyses, peridynamic material models have attracted significant interest, resulting in several 3D solid material models \cite{silling2007peridynamic, silling2005meshfree, gerstle2007peridynamic}.
+Similar models have been used to capture tension and compression in 1D bars\cite{silling2003deformation} and 2D membranes\cite{silling2005peridynamic}, but using them to model bending behavior requires a discretization with several nodes through the thickness of the feature, resulting in very computationally expensive models.
+A recent paper by Taylor and Steigmann \cite{taylor2013two} approaches this problem by reducing a bond based 3D plate to two dimensions with an integral through the plate's thickness.
+This creates a model that can represent thin structures with courser discretization.
+Although Taylor and Steigmann's model includes a bending term, it is demonstrated only for in-plane loading.
+The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
 
@@
 \label{sec:PDintro}
-\todo{Again, not word-for-word} The term \textit{peridynamic} alludes to the fact that the force at a point is affected by nearby material configuration and was coined by Silling to describe the new formulation of continuum mechanics he originally developed in \cite{silling2000reformulation}.
-Weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.
-These higher-order derivatives impose stronger continuity requirements than the classical models.
-By contrast, the peridynamic model is strongly nonlocal and casts material behavior at a point as the \textit{integral} equation
+Stewart Silling first developed the theory of peridynamics in~\cite{silling2000reformulation} to eliminate the problems associated with the undefined partial derivatives that attend the formation of cracks.
+The name refers to the force exerted on a point by material points a finite distance away.
+As a strongly nonlocal model, peridynamics casts material behavior at a point as the \textit{integral} equation
 %
@@
 Constitutive modeling of a wide variety of materials is accomplished by choosing the appropriate form for the force function.
-While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and other behaviors \cite{silling2005peridynamic, silling2007peridynamic, foster2010viscoplasticity, foster2011energy, jogrady2014a}\todo{Cite several more papers here.}.
+While the simplest force functions recreate a one-parameter linear elastic solid material \cite{silling2000reformulation}, other force functions can be used to model nonlinear elasticity, plasticity, damage, and many other behaviors \cite{silling2005peridynamic, dayal2006kinetics, gerstle2007peridynamic, silling2007peridynamic, warren2009non, foster2010viscoplasticity,foster2011energy,taylor2013two,ogrady2014beams}
 
 To describe force functionals that incorporate the behavior of a totality of points in the nearby material (not just $\mathbf{x}$ and $\mathbf{q}$), we must introduce the concept of a peridynamic \emph{state}.
-
 Introduced by Silling et al.\ \cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.
@@
     \label{eq:PDstateEoM}
-    \rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega (\vstate{T}{\mathbf{x}}{\mathbf{q}-\mathbf{x}}-\vstate{T}{\mathbf{q}}{\mathbf{x}-\mathbf{q}}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}),\notag
+    \rho(\mathbf{x})\ddot{\mathbf{u}}(\mathbf{x}) = \int_\Omega (\vstate{T}{\mathbf{x}}{\mathbf{q}-\mathbf{x}}-\vstate{T}{\mathbf{q}}{\mathbf{x}-\mathbf{q}}) dV_\mathbf{q}  + \mathbf{b}(\mathbf{x}),
 \end{equation}
@@
 
-Just as stress and strain are work conjugate, so too are the force and deformation vector-states for hyperelastic materials.
+Just as stress and strain are work conjugate, so too are the force and deformation vector states for hyperelastic materials.
 If the force state $\vstate{T}{}{}$ is always in the same direction as the deformation state $\vstate{Y}{}{}$, then the force exerted by a ``bond'' between points is in the same direction as the deformed bond, and the model is called \textit{ordinary}.
 Models in which they are not in the same direction are called \textit{non-ordinary}.
-Silling et al.\ discussed the possibility of such models in \cite{silling2010peridynamic}, but very little work has touched on their use.
+Silling et al.\ discussed the possibility of such models in \cite{silling2010peridynamic}, but little work has touched on their use.
 Foster et al.\ \cite{foster2010viscoplasticity} and Warren et al.\ \cite{warren2009non} showed that correspondence models, which approximate a deformation gradient and use it to calculate bond forces based on classical constitutive models, result in non-ordinary state based constitutive models for finite deformations.
+Recent work by O'Grady and Foster \cite{ogrady2014beams} uses a non-ordinary material model to simulate bending in 1D beams.
 %
@@
 \section{Model Development}
-Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond vector emanating from a point is connected by a rotational spring to its opposite emanating from that same point.
+Consider the material model illustrated in \cref{fig:SimpleBondpair} in which every bond vector $\boldsymbol{\xi} = \mathbf{q}-\mathbf{x}\: $ emanating from a point is connected by a rotational spring to its opposite emanating from that same point.
 These points and bonds are illustrated in the context of a plate in \cref{fig:BondPairPlate}.
@@
 %
-If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \todo{Need to define $\boldsymbol{\xi}$ somewhere} \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} and analyzed in \cite{jogrady2014a} by taking the Fr\'echet derivative.
+If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} and analyzed in \cite{jogrady2014a} by taking the Fr\'echet derivative.
 For the derivation and a description of the Fr\'echet derivative see \ref{sec:frechet}.
@@
 \begin{equation}
-    \kappa_1=\frac{\partial^2 z}{\partial x_1^2}, \kappa_2= \frac{\partial^2 z}{\partial x_2^2}, \kappa_3=\frac{\partial^2 z}{\partial x_1\partial x_2}\notag
+    \kappa_1=\frac{\partial^2 z}{\partial x_1^2}, \quad \kappa_2= \frac{\partial^2 z}{\partial x_2^2}, \quad \kappa_3=\frac{\partial^2 z}{\partial x_1\partial x_2}\notag
 \end{equation}
@@
 %\label{eq:continuousBeamw}
-    w =& \omega(\boldsymbol{\xi}) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) ) \right] \notag \\
-    =& \omega(\boldsymbol{\xi}) \alpha\frac{\xi^2}{8}(\kappa_1^2\cos^4(\phi)+\kappa_2^2\sin^4(\phi)+2\kappa_1\kappa_2\cos^2(\phi)\sin^2(\phi)+4\kappa_3^2\cos^2(\phi)\sin^2(\phi) \notag \\
-    & +4\kappa_1\kappa_3\cos^3(\phi)\sin(\phi)+4\kappa_2\kappa_3\cos(\phi)\sin^3(\phi))+\mathcal{O}(\xi^4).\notag
+    w &= \omega(\boldsymbol{\xi}) \alpha \left[1+\cos(\theta(\vstate{Y}{}{\boldsymbol{\xi}},\vstate{Y}{}{\boldsymbol{-\xi}}) ) \right] \notag \\
+    &= \omega(\boldsymbol{\xi}) \alpha\frac{\xi^2}{8}(\kappa_1^2\cos^4(\phi)+\kappa_2^2\sin^4(\phi)+2\kappa_1\kappa_2\cos^2(\phi)\sin^2(\phi)+4\kappa_3^2\cos^2(\phi)\sin^2(\phi) \notag \\
+    &+ 4\kappa_1\kappa_3\cos^3(\phi)\sin(\phi)+4\kappa_2\kappa_3\cos(\phi)\sin^3(\phi))+\mathcal{O}(\xi^4).\notag
 \end{align}
@@
     \lim_{\delta \to 0}  W &= \Omega, \notag \\
-    \alpha \frac{3 \pi}{8} m \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)&= \frac{G h^3}{12(1-\nu)} \left(\kappa_1^2+\kappa_2^2+2\nu\kappa_1\kappa_1+2(1-\nu)\kappa_3^2 \right), \notag \\
+    \alpha \frac{3 \pi}{8} m \left(\kappa_1^2+\kappa_2^2+\frac{2}{3}\kappa_1\kappa_1+\frac{4}{3}\kappa_3^2 \right)&= \left[ \frac{G h^3}{12(1-\nu)} \left(\kappa_1^2+\kappa_2^2+2\nu\kappa_1\kappa_1+2(1-\nu)\kappa_3^2 \right) \right]_{\nu=1/3}, \notag \\
 %    \nu = \frac{1}{3},\:\: \alpha &= \frac{8}{3 \pi m} \frac{G h^3}{12(1-\nu)},
-    \nu = \frac{1}{3},\:\: \alpha &= \frac{16}{3 m} \frac{G h^3}{12(1-\sfrac{1}{3})},
+    \alpha &= \frac{2 G h^3}{3 m}, \\
+    \text{with}\qquad \qquad \notag \\
     \label{eq:alpha}
+%    m = \int_{0}^{\delta} \omega(\xi) \xi^3 {\rm d}\xi \notag.
+    m &= \int_{0}^{\delta} \int_{0}^{2\pi}\omega(\xi) \xi^2 \xi {\rm d}\phi {\rm d}\xi \notag,
 \end{align}
 %
-with 
-\begin{equation}
-%    m = \int_{0}^{\delta} \omega(\xi) \xi^3 {\rm d}\xi \notag.
-    m = \int_{0}^{\delta} \int_{0}^{2\pi}\omega(\xi) \xi^2 \xi {\rm d}\phi {\rm d}\xi \notag.
-\end{equation}
-
+where $G$ is the shear modulus, $h$ is the thickness of the plate, and we have evaluated the classical Kirchoff strain-energy at a Poisson ratio of \(\sfrac{1}{3}\) in order to solve for alpha as a constant.
+Because $\alpha$ is inversely proportional to $m$, the energy does not change with varying choices for $\omega$ and $\delta$.
 It should be noted that the restriction \(\nu=\sfrac{1}{3}\) is the same imposed by the use of a bond based peridynamic model for in-plane deformation of a 2D peridynamic plate.
+We will show an extension to this model that removes this restriction in Section~\ref{sec:arbitrary}.
 
 \subsection{Combining Bending and Extension Models}
-The bond-pair bending model does not resist deformations that preserve the angles between opposite bonds\todo{This reads a little funny, could we not say: \ldots resist in-plane stretching or shear deformation.}, such as in-plane stretch or shear \todo{or you might just say: \dots does not develop membrane forces.}.
-If these behaviors are expected in combination with bending, a useful model must resist both.
+The bond-pair bending model does not resist in-plane stretching or shear deformation because these deformations preserve the angles between opposite bonds.
+\todo{This reads a little funny, could we not say: \ldots resist in-plane stretching or shear deformation.}\todo{or you might just say: \dots does not develop membrane forces.}  If these behaviors are expected in combination with bending, a useful model must resist both in-plane and transverse deformations.
 To create a plate model that also resists these deformations, i.e.\ a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from \cite{silling2000reformulation}.
@@
 %
-By matching the energy of a plate in shear deformation, we can relate \(\beta\) to the shear modulus and thickness of the plate.
-Following the example of \cite{silling2007peridynamic}, we begin with a plate \todo{should this be shell?} under pure in-plane shear.
-In Einstein notation, the strain energy of this plate is
+By matching the energy of a 2D material in shear deformation, we can relate \(\beta\) to the shear modulus and thickness of the shell.
+Following the example of \cite{silling2007peridynamic}, we begin with a 2D material under pure in-plane shear.
+In Einstein notation, the strain energy of this material is
 %
@@
 %
-With $i, j, k, l = 1,2$. For a circular $\omega$, combinations of $\{i,j,k,l\}$ with an odd number of any index, such as $\{1,1,1,2\}$ will integrate to 0.
+where $\epsilon^d$ is the deviatoric strain tensor.
+Now, to evaluate the integral we will exploit the symmetry properties.
+With $i, j, k, l = 1,2$.
+For a circular $\omega$, combinations of $\{i,j,k,l\}$ with an odd number of any index, such as $\{1,1,1,2\}$ will integrate to 0.
 %
@@
     m &= \int_A \omega(\xi)|\boldsymbol{\xi}|^2\; dA_{\boldsymbol{\xi}} \\
-    W^d_\text{PD} &= \frac{\beta \; m}{16}[3(\epsilon_{11}\epsilon_{11}+\epsilon_{22}\epsilon_{22})+(\epsilon_{11}\epsilon_{22}+\epsilon_{12}\epsilon_{12}+\epsilon_{12}\epsilon_{21}+\epsilon_{21}\epsilon_{12}+\epsilon_{21}\epsilon_{21}+\epsilon_{22}\epsilon_{11}]\\
+    W^d_\text{PD} &= \frac{\beta \; m}{16}[3(\epsilon_{11}\epsilon_{11}+\epsilon_{22}\epsilon_{22})+(\epsilon_{11}\epsilon_{22}+\epsilon_{12}\epsilon_{12}+\epsilon_{12}\epsilon_{21}+\epsilon_{21}\epsilon_{12}+\epsilon_{21}\epsilon_{21}+\epsilon_{22}\epsilon_{11})]\\
     &= \frac{\beta \; m}{16} \epsilon_{ij}^d \epsilon_{kl}^d (\delta_{ij}\delta_{kl}+\delta_{ik}\delta_{jl}+\delta_{il}\delta_{jk})\\
@@
 
-Combining the bending and extension models allows for the description of more complex behaviors, particularly the stiffening effect of in-plane tension on the transverse bending of a plate.
-Consider a single bond-pair in the combined model:
+Combining the bending and extension models allows for the description of more complex behaviors, particularly the stiffening effect of in-plane tension on the transverse bending of a shell.
+Consider a single bond-pair in the combined model shown in Fig.~\ref{fig:hybridmodel}.
 %
 \begin{figure}[tbp]
-  \label{fig:hybridmodel}
   \centering
@@
   \caption{The Hybrid Model Combines Bending and Extension Components}
+  \label{fig:hybridmodel}
 \end{figure}
@@
 \section{Extension to arbitrary Poisson ratio}
+\label{sec:arbitrary}
 Although many materials have Poisson ratios of \(\nu\approx \sfrac{1}{3}\), it is nonetheless desirable to extend the model to materials with arbitrary Poisson ratios.
@@
 The discrepancy in energy is proportional to the square of average curvature, \(\frac{\kappa_1+\kappa_2}{2} = \bar{\kappa}\), which we will also refer to as the isotropic curvature.
-The isotropic curvature can be envisioned as the portion of the deformation that resembles a spherical bowl.
+The isotropic curvature can be envisioned as the portion of the deformation that resembles a hemispherical bowl.
 A complete decomposition of bending energy into isotropic and deviatoric components as performed by Fischer in \cite{fischer1992bending} produces a far more complex model and is unnecessary at this time.
@@
 For large rotations, we can define an average curvature vector \(\bar{\boldsymbol{\kappa}}\).
-This leads us to estimate the average curvature as 
+This leads us to model the average curvature as 
 %
 \begin{align}
-    \bar{\boldsymbol{\kappa}} &= \frac{1}{m_2} \int_0^\delta \int_0^{2\pi}\psi(\xi)\frac{\vstate{Y}{}{\boldsymbol{\xi}}+\vstate{Y}{}{\boldsymbol{-\xi}}}{\xi^2} \xi {\rm d}\phi {\rm d}\xi ;\notag \\
-    m_2 &= \int_0^\delta \int_0^{2\pi}\psi(\xi)\xi {\rm d}\phi {\rm d}\xi. \notag
+    \bar{\boldsymbol{\kappa}} &= \frac{1}{m} \int_0^\delta \int_0^{2\pi}\omega(\xi)\frac{\vstate{Y}{}{\boldsymbol{\xi}}+\vstate{Y}{}{\boldsymbol{-\xi}}}{\xi^2} \xi {\rm d}\phi {\rm d}\xi ;\notag \\
+    m &= \int_0^\delta \int_0^{2\pi}\omega(\xi)\xi {\rm d}\phi {\rm d}\xi. \notag
 \end{align}
 %
-The weighting function \(\psi(\xi)\) performs a role similar to that of \(\omega(\xi)\) from the previous section, but need not be identical.
+The weighting function \(\omega(\xi)\) performs the same function as in the previous section.
 We can rewrite the energy discrepancy in terms of \(\bar{\boldsymbol{\kappa}}\).
@@
 \begin{equation}
-    W'=2G\frac{h^3}{12}\frac{3\nu-1}{1-\nu}\frac{\bar{\boldsymbol{\kappa}}^2}{2}. \notag
+    W'=2G\frac{h^3}{12}\frac{3\nu-1}{1-\nu}\bar{\boldsymbol{\kappa}}^2. \notag
 \end{equation}
 %
-We can take the Fr\'{e}chet derivative to produce a correction force vector state
+We can take the Fr\'{e}chet derivative (details in \ref{sec:frechet})\todo{Can you show the details in the Appendix?  Also, should the $dA$ be there?} to produce a correction force vector state
 %
 \begin{equation}
-    \vstate{T'}{}{\boldsymbol{\xi}}=\frac{4G}{m_2}\frac{h^3}{12}\frac{3\nu-1}{1-\nu}\frac{\psi(\boldsymbol{\xi})}{\xi^2} \bar{\boldsymbol{\kappa}}\;dA,
+    \vstate{T'}{}{\boldsymbol{\xi}}=\frac{8G}{m}\frac{h^3}{12}\frac{3\nu-1}{1-\nu}\frac{\omega(\boldsymbol{\xi})}{\xi^2} \bar{\boldsymbol{\kappa}},
     \label{eq:pressureState}
@@
 This ``pressure'' is proportional to the curvature vector at that node.
-A weighting function \(\psi(\boldsymbol{\xi}) = |\boldsymbol{\xi}|\) can ensure that the integral expression for force at a point is convergent.
-This extra term that is dependent on the bending of all the pairs around a node means that the extension is not properly a \textit{bond-pair} model.
+A weighting function \(\omega(\boldsymbol{\xi}) = |\boldsymbol{\xi}|\) can ensure that the integral expression for force at a point is convergent.
+This extra term that is dependent on the bending of all the pairs around a material point means that the extension is not properly a \textit{bond-pair} model.
 Instead, it would be more accurate to call it a \textit{bond-multiple} model, in which the bond forces and energies are functions of the relationship between a family of bonds.
@@
 \begin{align}
-    \label{eq:discretebeam}
+%    \label{eq:discretebeam}
     \alpha &= \frac{c\; (\Delta x)^2}{m} ;\; c= \frac{G}{(1-\nu)}\frac{h^3}{12};\; m=\sum_{i=1}^n \omega(\boldsymbol{\xi}_i)\boldsymbol{\xi}_i^2 \implies \nonumber \\
@@
 \begin{align}
+    \label{eq:discreteEoM}
     \rho(\mathbf{x})\mathbf{\ddot{u}}(\mathbf{x}) = \mathbf{f}(\mathbf{x})&+\sum_i \omega(\boldsymbol{\xi}_i)\left\{\frac{\alpha(\mathbf{x})}{|\mathbf{p}_i |}\frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \left[ \frac{\mathbf{p}_i}{|\mathbf{p}_i |}\times \frac{\mathbf{q}_i}{|\mathbf{q}_i |}\right] \right.
-\notag \\
+\\
     & \left.
@@
 \begin{align*}
-    \bar{\boldsymbol{\kappa}}(\mathbf{x}) &= \frac{1}{m_2} \sum_i \psi(\boldsymbol{\xi}_i)\frac{\mathbf{p}_i +\mathbf{q}_i }{\boldsymbol{\xi}_i^2};\notag \\
-    m_2(\mathbf{x})  &= \sum_i \psi(\boldsymbol{\xi}_i); \notag \\
-    \alpha^\text{iso}(\mathbf{x}) &= \frac{4G}{m_2}\frac{h^3}{12}\frac{3\nu-1}{1-\nu}(\Delta x)^2;\\
+    \bar{\boldsymbol{\kappa}}(\mathbf{x}) &= \frac{1}{m} \sum_i \omega(\boldsymbol{\xi}_i)\frac{\mathbf{p}_i +\mathbf{q}_i }{\boldsymbol{\xi}_i^2};\notag \\
+    m(\mathbf{x})  &= \sum_i \omega(\boldsymbol{\xi}_i); \notag \\
+    \alpha^\text{iso}(\mathbf{x}) &= \frac{4G}{m}\frac{h^3}{12}\frac{3\nu-1}{1-\nu}(\Delta x)^2;\\
     f^\text{iso}(\mathbf{x}) &= \sum_j \left\{\left[\alpha^\text{iso}(\mathbf{x})\bar{\boldsymbol{\kappa}}(\mathbf{x})-\alpha^\text{iso}(\mathbf{x}+\boldsymbol{\xi}_j)\bar{\boldsymbol{\kappa}}(\mathbf{x}+\boldsymbol{\xi}_j) \right] \frac{\omega(\boldsymbol{\xi}_j)}{\boldsymbol{\xi}_j^2} \right\}
@@
 %
-Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced throughout the entire plate, otherwise the displacement \(z(\mathbf{x}-\boldsymbol{\xi}_i)\) is ill-defined. 
+Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced, $\Delta x$, throughout the entire plate, otherwise the displacement \(z(\mathbf{x}-\boldsymbol{\xi}_i)\) is ill-defined.
 For this reason, the discretization does not allow for areas of higher and lower ``resolution''.
+An extension to this discretization that would allow changing mesh resolution will require interpolation between the nodes.
 %
@@
 
-Additionally, the simply-supported flat plate is a configuration with significant analytical treatment, making a better comparison case than configurations that may require comparison to finite element or other solution techniques.
+Additionally, the simply-supported flat plate is a configuration with significant analytical treatment in the classical theories, making a better comparison case than configurations that may require comparison to finite element or other solution techniques.
 %
@@
 The simplest test case for this model is a linear-elastic square plate with Poisson's ratio \(\nu = \sfrac{1}{3}\) that is simply-supported on all 4 sides with a uniform transverse pressure load on the entire surface between the supports.
-As expected from an energy-equivalent model, the slice along the plate's centerline shown in \cref{fig:elastic_plate} demonstrates good agreement between the static deflection predicted by the bond-pair model and that of classical linear elasticity.
+As expected from an energy-equivalent model, the slice along the plate's centerline shown in \cref{fig:plate_convergence_h} demonstrates good agreement between the static deflection predicted by the bond-pair model and that of classical linear elasticity as the horizon length shrinks.
+This convergence only continues to a minimum horizon, below which the discretized equation of motion (\cref{eq:discreteEoM}) ceases to accurately approximate the continuous integral formulation (\cref{eq:PDstateEoM,eq:SillingForceNO}).
+The minimum horizon size depends on the discretization; it appears that twice the node spacing is insufficient, and that three times the node spacing is sufficient.
+The difference is evident in \cref{fig:plate_minimum_h}.
+%
+\begin{figure}[h]
+  \centering
+  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_convergence_h.pgf}}
+  \caption{The Bond-Pair Model Converges on Accurate Plate Deflection with Smaller Horizons}
+  \label{fig:plate_convergence_h}
+\end{figure}
+%
+\begin{figure}[h]
+  \centering
+  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_minimum_h.pgf}}
+  \caption{Horizon Must Include Sufficient Nodes}
+  \label{fig:plate_minimum_h}
+\end{figure}
+%
 Accurate results require a denser discretization than is the case for the elastic beams from previous work.
-
+\Cref{fig:plate_convergence_n} illustrates the model converging to the analytical solution as the discretization is made finer.
 %
@@
 Normalized to the the maximum displacement of a transversely-loaded plate with no in-plane edge loads, the results in \cref{fig:plateStiffening} show that the hybrid model does a good job of simulating the impact of in-plane tension on maximum transverse deflection.
-
+%
 \begin{figure}[tbp]
@@
 \end{figure}
-
+%
 The bond-multiple plate model is motivated by the desire to extend the bending model to an arbitrary Poisson's ratio, so the obvious test for this model is the same as for the bond-pair model.
 When compared to analytical predictions, \cref{fig:plate_poisson} demonstrates the bond-multiple model's ability to simulate plates with Poisson's ratios that depart significantly from the bond-pair limitation of $\nu = \sfrac{1}{3}$.
-
+%
 \begin{figure}[tbp]
@@
 \end{figure}
+%
+
+Although these elastic examples demonstrate the accuracy of the peridynamic model for simple bending, the defining feature of peridynamic models is the ability to simulate discontinuity and failure.
+To model simple brittle failure, a critical angle is computed for each bond pair based on the lengths of the connected bonds and the material and discretization properties.
+When a bond pair exceeds the critical deformation angle, its stiffness is set to 0 for the rest of the simulation.
+To demonstrate the behavior of this model, a controlled-displacement double-torsion fracture test was simulated with the bond-pair model.
+A good review of the double-torsion test is available in \cite{shyam2006double}.
+The simple qualitative results are shown in \cref{fig:DTdamage}, colored by the fraction of failed bond pairs around each node.
+For each successive displacement load, the stable progression of the damaged region extends further into the plate.
+
+%
+\begin{figure}[tbp]
+  \centering
+  \resizebox{0.6\linewidth}{!}{\input{\plotpath/DoubleTorsionDamage.pgf}}
+  \caption{Crack Progression in Double Torsion Brittle Plate}
+  \label{fig:DTdamage}
+\end{figure}
+%
+
+This result is intended to be a qualitative demonstration of potential rather than an in-depth analysis of the brittle failure model.
+A more thorough treatment of this and other failure models will be the subject of future work.
 
 \section{Conclusion}
-
 The non-ordinary bond-pair model is the first peridynamic material model to directly resist bending deformation.
@@
 Calculating isotropic bending and extension states allows for a straightforward extension of both models to account for isotropic deformation energy and enables accurate modeling of plates with arbitrary Poisson's ratios.
+A demonstration of brittle fracture in a bending plate shows the potential of this model to broaden the class of problems that can realistically be modeled using peridynamics.
 
@@
 \label{sec:frechet}
-
+\subsection{Definition}
 The derivative of a function of a state is defined by Silling in \cite{silling2007peridynamic} as follows:
@@
 \end{equation}
-Then $\Psi$ is said to be \textit{differentiable} and $\nabla\Psi$ is called the \textit{Frechet derivative} of $\Psi$.
+Then $\Psi$ is said to be \textit{differentiable} and $\nabla\Psi$ is called the \textit{Fr\'echet derivative} of $\Psi$.
 \end{quote}
-This is a fairly straightforward way of defining a derivative with respect to a state, and we will apply it to derive the bond force function from the bond-pair energy function
+This is a fairly straightforward way of defining a derivative with respect to a state.
+Because the force vector-state and deformation vector-state are work conjugate, the force vector-state can be determined by taking the Fr\'echet derivative of energy with respect to the deformation vector-state.
+\subsection{Bond-Pair Force}
+For the bond-pair model, we derive the bond force function from the bond-pair energy function
 %
@@
 %
+\subsection{Isotropic Bending Correction}
+To derive the bending ``pressure'' force, we start with the isotropic energy discrepancy
+%
+\begin{equation}
+    W'=2G\frac{h^3}{12}\frac{3\nu-1}{1-\nu}\bar{\boldsymbol{\kappa}}^2. \notag
+\end{equation}
+%
+with
+%
+\begin{align}
+    \bar{\boldsymbol{\kappa}}\left(\vstate{Y}{}{}\right) &= \frac{1}{m} \int_0^\delta \int_0^{2\pi}\omega(\xi)\frac{\vstate{Y}{}{\boldsymbol{\xi}}+\vstate{Y}{}{\boldsymbol{-\xi}}}{\xi^2} \xi {\rm d}\phi {\rm d}\xi \notag \\
+    &= \frac{2}{m} \int_0^\delta \int_0^{2\pi}\omega(\xi)\frac{\vstate{Y}{}{\boldsymbol{\xi}}}{\xi^2} \xi {\rm d}\phi {\rm d}\xi \notag
+\end{align}
+Because $\bar{\boldsymbol{\kappa}}$ is itself a vector-state, we will need to begin with the change in $\bar{\boldsymbol{\kappa}}$ with respect to $\vstate{Y}{}{}$ and carry the result through to find the change in $W'$.
+\begin{align}
+    \bar{\boldsymbol{\kappa}}\left(\vstate{Y}{}{}+\Delta\vstate{Y}{}{}\right) &= \frac{2}{m} \int_0^\delta \int_0^{2\pi}\omega(\xi)\frac{\vstate{Y}{}{\boldsymbol{\xi}}+\Delta\vstate{Y}{}{\boldsymbol{\xi}}}{\xi^2} \xi {\rm d}\phi {\rm d}\xi \notag \\
+    &= \bar{\boldsymbol{\kappa}}\left(\vstate{Y}{}{}\right) + \frac{2}{m} \int_0^\delta \int_0^{2\pi}\omega(\xi)\frac{\Delta\vstate{Y}{}{\boldsymbol{\xi}}}{\xi^2} \xi {\rm d}\phi {\rm d}\xi \notag 
+\end{align}
+%
+%
+\begin{align}
+    W'\left(\vstate{Y}{}{}+\Delta\vstate{Y}{}{}\right) &=2G\frac{h^3}{12}\frac{3\nu-1}{1-\nu}\left[\bar{\boldsymbol{\kappa}}\!\left(\vstate{Y}{}{}+\Delta\vstate{Y}{}{}\right)\right]^2 \notag \\
+    &=2G\frac{h^3}{12}\frac{3\nu-1}{1-\nu} \left\{ \vphantom{\int_0^\delta} \bar{\boldsymbol{\kappa}}\!\left(\vstate{Y}{}{}\right) \cdot \bar{\boldsymbol{\kappa}}\!\left(\vstate{Y}{}{}\right)\right.
+\notag \\
+    &\phantom{=2G\frac{h^3}{12}\frac{3\nu-1}{1-\nu}} + \frac{4}{m} \int_0^\delta \int_0^{2\pi}\omega(\xi)\frac{\Delta\vstate{Y}{}{\boldsymbol{\xi}}\cdot \bar{\boldsymbol{\kappa}}\!\left(\vstate{Y}{}{}\right)}{\xi^2} \xi {\rm d}\phi {\rm d}\xi \notag \\
+    &\phantom{=2G\frac{h^3}{12}\frac{3\nu-1}{1-\nu}}\left.
++ \frac{2}{m} \int_0^\delta \int_0^{2\pi}\omega(\xi)\frac{\Delta\vstate{Y}{}{\boldsymbol{\xi}}\cdot \Delta\vstate{Y}{}{\boldsymbol{\xi}}}{\xi^2} \xi {\rm d}\phi {\rm d}\xi\right\} \notag \\
+    &=W'\left(\vstate{Y}{}{}\right)+ 2G\frac{h^3}{12}\frac{3\nu-1}{1-\nu} \frac{4}{m} \frac{\omega(\xi)}{\xi^2} \bar{\boldsymbol{\kappa}}\!\left(\vstate{Y}{}{}\right) \bullet \Delta\vstate{Y}{}{} + o\left(||\Delta\vstate{Y}{}{}||\right)\notag \\
+    \nabla W'\!\left(\vstate{Y}{}{}\right) &= \vstate{T}{}{\boldsymbol{\xi}} =  \frac{8 G}{m} \frac{h^3}{12}\frac{3\nu-1}{1-\nu}\frac{\omega(\xi)}{\xi^2} \bar{\boldsymbol{\kappa}}\notag
+\end{align}
+%
+This demonstrates the bond-length dependent ``pressure'' applied to each point in the neighborhood of a point with average curvature $\bar{\boldsymbol{\kappa}}$.
 

### 2014-05-13 PlatePaper.tex
added displacement to double torsion plots
version submitted to IJSS

@@
 \begin{abstract}
-This paper builds on the peridynamic state based beam model to represent the bending of a Kirckhoff-Love plate.
+This paper builds on the peridynamic state-based beam model to represent the bending of a Kirckhoff-Love plate.
 This model is non-ordinary and derived from the concept of a rotational spring between bonds.
@@
 \begin{keyword}
-peridynamics \sep non-ordinary model \sep non-local model
+peridynamics \sep non-ordinary model \sep non-local model \sep non-local plate
 \end{keyword}
@@
 %
-If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} and analyzed in \cite{jogrady2014a} by taking the Fr\'echet derivative.
+If we call the deformed angle between these bonds \(\theta\), and choose the potential energy of that spring to be \(w(\boldsymbol{\xi}) = \omega(\boldsymbol{\xi})\alpha [1 + \cos(\theta) ] \) for the bond pair $\boldsymbol{\xi}$ and $-\boldsymbol{\xi}$, we can recover the non-ordinary force state proposed by Silling in \cite{silling2007peridynamic} and analyzed in \cite{ogrady2014beams} by taking the Fr\'echet derivative.
 For the derivation and a description of the Fr\'echet derivative see \ref{sec:frechet}.
@@
 \end{align}
-\todo{It's a little unclear how $m$ arrises below from this equation.  Please see if you can make it more clear.} 
 %
@@
 The bond-pair bending model does not resist in-plane stretching or shear deformation because these deformations preserve the angles between opposite bonds.
-\todo{This reads a little funny, could we not say: \ldots resist in-plane stretching or shear deformation.}\todo{or you might just say: \dots does not develop membrane forces.}  If these behaviors are expected in combination with bending, a useful model must resist both in-plane and transverse deformations.
+If these behaviors are expected in combination with bending, a useful model must resist both in-plane and transverse deformations.
 To create a plate model that also resists these deformations, i.e.\ a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from \cite{silling2000reformulation}.
@@
 For a single bond pair we can represent the curvature vector along the bond pair as
-%\marginpar{ maybe leave this out and go straight to the curvature vector?}
 %
@@
 \end{equation}
-%
-%\begin{equation}
-%    \kappa_{\hat{u}} = \frac{z(\mathbf{x}+\xi\hat{u})-2z(\mathbf{x})+z(\mathbf{x}-\xi\hat{u})}{\xi^2}\notag
-%\end{equation}
 %
@@
 %
-We can take the Fr\'{e}chet derivative (details in \ref{sec:frechet})\todo{Can you show the details in the Appendix?  Also, should the $dA$ be there?} to produce a correction force vector state
+We can take the Fr\'{e}chet derivative (details in \ref{sec:frechet}) to produce a correction force vector state
 %
@@
 \begin{align}
-%\label{eq:discreteBeamw}
 w(\boldsymbol{\xi}_i) &= \omega(\boldsymbol{\xi}_i)\alpha \left[1+\cos(\theta(\vstate{Y}{}{\boldsymbol{\xi}_i},\vstate{Y}{}{-\boldsymbol{\xi}_i})) \right] \notag \\
@@
 \begin{align}
-%    \label{eq:discretebeam}
     \alpha &= \frac{c\; (\Delta x)^2}{m} ;\; c= \frac{G}{(1-\nu)}\frac{h^3}{12};\; m=\sum_{i=1}^n \omega(\boldsymbol{\xi}_i)\boldsymbol{\xi}_i^2 \implies \nonumber \\
@@
   \centering
-  \resizebox{0.6\linewidth}{!}{\input{\plotpath/DoubleTorsionDamage.pgf}}
+  \resizebox{0.8\linewidth}{!}{\input{\plotpath/DoubleTorsionDD.pgf}}
   \caption{Crack Progression in Double Torsion Brittle Plate}

### 2014-07-31 response/response.tex
add review response and changes made in response to reviewer comments

\documentclass{article}
\usepackage[left=1.0in,right=1.0in,top=1.0in,bottom=1.0in]{geometry}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage[normalem]{ulem}
\usepackage{cancel}
\definecolor{light-gray}{gray}{0.5}

\begin{document}

\begin{center}
    {\LARGE \bf Point-by-Point Response to Reviewer's Comments} \\
     Author's Responses in {\color{red} Red}
\end{center}

%%%% First Reviewer %%%%
\section{Reviewer}
%
\subsection*{Specific Comments}

\begin{enumerate}
%
   \item This review took me a long time because I had to first read through Taylor and Steigman (Ref [6]).  After reading [6], I am unsure if the current manuscript is a significant advance.  First, I'll point an error in the text referencing [6] -- this manuscript claims that [6] does not simulate bending but that is incorrect.  Their numerical example indeed is of applied tensile loading, but due to the complex stress distribution, there is wrinkling and out-of-plane deflection which necessarily implies bending.  This should be corrected.  But a bigger question is why the approach in this paper when [6] exists.  [6] has only been applied to bond-based peridynamics, but it is readily extendable to the state-based models.  That approach provides a much more systematic approach to reduce to 3D.  In this paper, one has to compare with standard continuum models and do energy matching.  Suppose one were in a situation where one is unsure of the correct continuum model (e.g. thick
shells).  Then what do we compare it with?  The approach in [6] has no such issues.
   {\color{red}
     \begin{itemize}
        \item Changed reference to directly mention transverse wrinkling:
        \begin{quote}This creates a model that can represent thin structures and includes a bending term, \underline{which resists transverse wrinkling behavior in a simulation of} tension loading.
        \end{quote}
        \item There are two major factors that make this paper important. 
        First, the submitted manuscript is clearly original through it’s use of non-ordinary peridynamic material models which have seen little attention in literature (excepting the so-called “correspondence models” which wrap classical stress-strain constitutive laws, here we are referring to “native” peridynamic materials). Only the previous paper on peridynamic beams [15] has applied non-ordinary models to useful engineering practice. These non-ordinary models with their ability to resist rotation and other complex deformations, have no analog in classical continuum mechanics. This alone merits scientific exploration. While here we are using them for plates and shells, their utility could far exceed these simple models. This work lays the foundation for more complex explorations of material behavior in the future. While both the submitted manuscript and [6] arrive at useful models for peridynamic plates and shells, the approach is clearly very different.

        Second, while the asymptotic approach can be applied to state-based theory, it is not done in [6]. The reason to use a state-based model would be to develop material descriptions capable of modeling materials with arbitrary Poisson ratio. The Poisson ratio of the model developed in [6] is fixed at 1/3, as are all 2D bond-based models. Our model allows for material models of arbitrary Poisson ratio and correctly reproduces the classical results in the limit of vanishing $\delta$. In order to model arbitrary Poisson ratio in a nonlocal model requires a term we we call the “isotropic curvature” in our paper. Because state-based models use functions that describe the totality of deformations of all points in a materials horizon, the “isotropic curvature” is a function of not only the neighbors of $x$, but also the neighbors of $x'$. Following the procedure of [6] would require a Taylor expansion through the thickness of the material, then along the plane about $x'' = x'$, and then a second Taylor expansion through the thickness and integration around $x$. The tractability of this procedure leads us to question how “readily extensible” the approach of [6] is.
     \end{itemize}
%        \begin{align*}
%        \rho \left(\mathbf{\ddot{u}}_0+\zeta \mathbf{\ddot{a}}+\frac{1}{2}\zeta^2\mathbf{\ddot{b}}+\frac{1}{2}\zeta^3 \mathbf{\ddot{c}}+o(\zeta^3)\right) &= \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \mathbf{f}(\eta,\xi,\theta) d\zeta' dA'\notag \\
%        \theta(\xi) &=  \frac{3}{m} \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \omega(|\xi'|)(\xi'\cdot\eta') \notag \\
%        \frac{\partial\theta}{\partial \zeta'} &= \frac{3}{m} \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \omega(|\xi'|)(\xi'\cdot\frac{\partial \eta'}{\partial \zeta'}) \notag\\
%        \end{align*}
%        \begin{equation}
%        \frac{\partial\theta}{\partial \zeta'} = \frac{3}{m} \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \omega(|v''|)\xi''\cdot\left[a''(v'+v'')-a'(v')+(\zeta'+\zeta'')b''(v'+v'')-\zeta'b'(v')\right] d\zeta''dA'' \notag\\
%        \end{equation}
	}
  \item A minor issue is on page 10-11.  What is a "circular" $\omega$?  Do you mean it is a function only of $|\xi|$?  Please clarify.  Also clarify what you mean by "odd number of any index".
   {\color{red}
     \begin{itemize}
        \item Made more explicit:
        \quote{For a circular $\omega(\xi) = \omega(|\xi|)$, combinations of $\{i,j,k,l\}$ with an odd number of each index, such as $\{1,1,1,2\}$ or $\{2,1,2,2\}$, will result in odd powers of sine and cosine and integrate to 0.}
     \end{itemize}}
%
  \item The Appendix on Frechet derivatives is not required; you can simply refer to [1].
  {\color{red}
     \begin{itemize}
        \item response
     \end{itemize}}
%
     \item The title says "plates and flat shells".  What are flat shells??
  {\color{red}
     \begin{itemize}
        \item Shell models resist in-plane or membrane deformations, as opposed to plates, which resist only transverse deformations. This is noted on page 10:
        \quote{To create a plate model that also resists these deformations, i.e. a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from [10].}
     \end{itemize}}
%
\end{enumerate}
%
\subsection*{General Statement}
In essence, the main difficulty that I have in recommending acceptance is that I do not see this as a significant advance beyond [6].  Perhaps a chance to respond to this and a second round of review will clarify this.

\section{Reviewer}
\subsection*{General Statement}
The manuscript is a well-written account of developing a model of plates/shells within the peridynamic mechanic theory.

I have several minor comments and one final comment that is not so minor but can be addressed.
%
\subsection*{Specific Comments}

\begin{enumerate}

  \item The authors several times use the phrase "ill-defined". Probably more apt is "undefined". Jump discontinuities are undefined witinh the classical elastic theory.
%
     {\color{red}
     \begin{itemize}
        \item Changed in all locations
     \end{itemize}}
%
  \item Page 4 uses the phrase "to eliminate" when "mitigate" is more appropriate.
%
     {\color{red}
     \begin{itemize}
        \item Changed
     \end{itemize}}
%
  \item Pg 5. I don't think we "must" use the concept of peridynamic states. This is  choice. The paper http://dx.doi.org/10.1007/s10659-012-9418-x discusses an alternative formulation of the peridynamic equations for linear elasticity, and is able to precisely describe the class of deformations. And so there is a deeper concept lurking that "must" be modeled.
%
     {\color{red}
     \begin{itemize}
        \item Eliminated word ``must''
     \end{itemize}}
%
  \item The authors write "This convergence only continues to a minimum horizon, below which the discretized equation of motion (eq. (9)) ceases to accurately approximate the continuous integral formulation (eqs. (1) and (3)). The minimum horizon size depends on the discretization; it appears that twice the node spacing is insufficient, and that three times the node spacing is insufficient." These two sentences suggest that something is awry with the discretization. It seems as if the simple replacement of integrals with sums  is simply to simple to be viable since the horizon depends upon the particle density. Shouldn't these two parameters be separated? Can the authors hold the horizon fixed and let the particle density increase? Except for the potential cost, this would settle the question. Maybe it's a good idea to point out that better numerical methods are needed? Again, the paper http://dx.doi.org/10.1007/s10659-012-9418-x describes a variational formulation; wouldn't this
form a basis for a conforming FEM?
%
     {\color{red}
     \begin{itemize}
        \item Replaced figure 6 to show the effect of changing particle density with fixed horizon size. With more cases plotted, it is clearer that results are independent of particle density above a minimum threshold.
        \item Edited referring sentence to explain the updated plot:
        \begin{quotation}
        The difference is evident in fig. 6, which also shows that results are insensitive to fineness of discretization once the minimum horizon criterion is met.
        \end{quotation}
     \end{itemize}}
%
\end{enumerate}

\end{document}

### 2014-08-01 response/response.tex
added math to review response, responded to other review points

@@
         \item Changed reference to directly mention transverse wrinkling:
-        \begin{quote}This creates a model that can represent thin structures and includes a bending term, \underline{which resists transverse wrinkling behavior in a simulation of} tension loading.
+        \begin{quote}This creates a model that can represent thin structures and includes a bending term, \underline{which resists transverse wrinkling behavior in a simulation of crack growth under} tension loading.
         \end{quote}
-        \item There are two major factors that make this paper important. 
+        \item There are two major factors that make this paper important, even though [6] covers some of the same behavior.
 First, the submitted manuscript is clearly original through it’s use of non-ordinary peridynamic material models which have seen little attention in literature (excepting the so-called “correspondence models” which wrap classical stress-strain constitutive laws, here we are referring to “native” peridynamic materials).
@@
 In order to model arbitrary Poisson ratio in a nonlocal model requires a term we we call the “isotropic curvature” in our paper.
-Because state-based models use functions that describe the totality of deformations of all points in a materials horizon, the “isotropic curvature” is a function of not only the neighbors of $x$, but also the neighbors of $x'$.
-Following the procedure of [6] would require a Taylor expansion through the thickness of the material, then along the plane about $x'' = x'$, and then a second Taylor expansion through the thickness and integration around $x$.
-The tractability of this procedure leads us to question how “readily extensible” the approach of [6] is.
+Following the example of [1], we will call the dilation state $\theta$, and show how its incorporation is nontrivial.
+        \begin{equation*}
+        \rho \left(\mathbf{\ddot{u}}_0+\zeta \mathbf{\ddot{a}}+\frac{1}{2}\zeta^2\mathbf{\ddot{b}}+\frac{1}{2}\zeta^3 \mathbf{\ddot{c}}+o(\zeta^3)\right) = \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \mathbf{f}(\eta,\xi,\theta) d\zeta' dA' \tag{17'}
+        \end{equation*}
+        Because state-based models use functions that describe the totality of deformations of all points in a materials horizon, the dilation is a function of not only the neighbors of $x$, but also the neighbors of $x'$.
+        Following the procedure of [6] would require an additional Taylor expansion through the thickness of the material,
+        \begin{align*}
+        \theta(\boldsymbol{\xi}) &= \theta_0(\mathbf{v}) + \zeta\boldsymbol{\alpha}(\mathbf{v})+\frac{1}{2}\zeta^2\boldsymbol{\beta}(\mathbf{v})+o(\zeta^3) \notag \\
+        \end{align*}
+        followed by either a nested integral over the material plane, or a Taylor expansion along the plane about $x'' = x'$.
+        \begin{align*}
+        \theta(\xi) &=  \frac{3}{m} \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \omega(|\xi'|)(\xi'\cdot\eta') \notag \\
+        \boldsymbol{\alpha} = \frac{\partial\theta}{\partial \zeta'} &= \frac{3}{m} \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \omega(|\xi'|)(\xi'\cdot\frac{\partial \eta'}{\partial \zeta'}) \notag\\
+        \end{align*}
+        With the introduction of a dilation term $\theta$, Equation (29) gets an additional term:
+        \begin{equation*}
+        	\frac{G}{\partial\zeta'}(\zeta') = 
+	\left(\frac{\partial\mathbf{f}}{\partial\eta_0}\right)\frac{\partial\eta_0}{\partial\zeta'} +
+	\left(\frac{\partial\mathbf{f}}{\partial\xi_0}\right)\frac{\partial\xi_0}{\partial\zeta'} + 
+	\left(\frac{\partial\mathbf{f}}{\partial\theta_0}\right)\frac{\partial\theta_0}{\partial\zeta'} \tag{29'}
+        \end{equation*}
+        \begin{equation}
+        \frac{\partial\theta}{\partial \zeta'} = \frac{3}{m} \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \omega(|\mathbf{v}''|)\left[\mathbf{v}''+\zeta''\mathbf{k}\right]\cdot\left[\mathbf{a}''(\mathbf{v}'+\mathbf{v}'')-\mathbf{a}'(\mathbf{v}')+(\zeta'+\zeta'')\mathbf{b}''(\mathbf{v}'+\mathbf{v}'')-\zeta'\mathbf{b}'(\mathbf{v}')\right] d\zeta''dA'' \notag\\
+        \end{equation}
+        \begin{equation}
+        \frac{\partial\theta_0}{\partial \zeta'} = \frac{3}{m} \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \omega(|\mathbf{v}''+\zeta''\mathbf{k}|)\left[\mathbf{v}''+\zeta''\mathbf{k}\right]\cdot\left[\mathbf{a}''(\mathbf{v}'+\mathbf{v}'')-\mathbf{a}'(\mathbf{v}')+(\zeta'')\mathbf{b}''(\mathbf{v}'+\mathbf{v}'')\right] d\zeta''dA'' \tag{30'c}\\
+        \end{equation}
+         These terms end up inside the larger integrals of equations (37) and (43).
+While it may be possible to simplify the relationship between $\mathbf{u}$, $\mathbf{a}$, and $\theta$, the tractability of this procedure leads us to question how “readily extensible” the approach of [6] is.
      \end{itemize}
-%        \begin{align*}
-%        \rho \left(\mathbf{\ddot{u}}_0+\zeta \mathbf{\ddot{a}}+\frac{1}{2}\zeta^2\mathbf{\ddot{b}}+\frac{1}{2}\zeta^3 \mathbf{\ddot{c}}+o(\zeta^3)\right) &= \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \mathbf{f}(\eta,\xi,\theta) d\zeta' dA'\notag \\
-%        \theta(\xi) &=  \frac{3}{m} \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \omega(|\xi'|)(\xi'\cdot\eta') \notag \\
-%        \frac{\partial\theta}{\partial \zeta'} &= \frac{3}{m} \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \omega(|\xi'|)(\xi'\cdot\frac{\partial \eta'}{\partial \zeta'}) \notag\\
-%        \end{align*}
-%        \begin{equation}
-%        \frac{\partial\theta}{\partial \zeta'} = \frac{3}{m} \int\limits_{\Omega} \int\limits_{0}^{\epsilon} \omega(|v''|)\xi''\cdot\left[a''(v'+v'')-a'(v')+(\zeta'+\zeta'')b''(v'+v'')-\zeta'b'(v')\right] d\zeta''dA'' \notag\\
-%        \end{equation}
 	}
@@
      \begin{itemize}
-        \item response
+        \item While a reference to [1] provides readers with all the necessary tools to verify our derivations, those unfamiliar with Fr\'echet derivatives will find it far easier to follow the appendix.
+Because readers are not yet accustomed to this sort of evaluation, especially for trigonometric and compound vector states, we feel that retaining the appendix is a solid compromise between keeping the body of the paper readable and allowing interested readers to quickly verify or imitate our derivations.
      \end{itemize}}
@@
 Maybe it's a good idea to point out that better numerical methods are needed?
-Again, the paper http://dx.doi.org/10.1007/s10659-012-9418-x describes a variational formulation; wouldn't this
-form a basis for a conforming FEM?
+Again, the paper http://dx.doi.org/10.1007/s10659-012-9418-x describes a variational formulation; wouldn't this form a basis for a conforming FEM?
 %
@@
         \end{quotation}
+        \item The focus of this paper is the model rather than the numerical methods, so we try to leave criticism of existing numerical methods to those working to remedy the situation.
+That said, using nonlocal vector calculus as the basis of an FEM would seem to handle nonlocality/scale effects, but risks reintroducing mesh dependence to failure analyses.
      \end{itemize}}

### 2014-08-01 PlatePaper.tex
added math to review response, responded to other review points

@@
 Modeling material failure is one of the most common challenges in mechanical engineering analysis.
-When processes such as fracture are modeled, the partial-differential equations of classical mechanics are ill-defined at the resulting discontinuities in displacement.
+When processes such as fracture are modeled, the partial-differential equations of classical mechanics are undefined at the resulting discontinuities in displacement.
 A peridynamic formulation of continuum mechanics casts material behavior in terms of integral functions of displacement (as opposed to gradients of displacement), so that discontinuities can evolve naturally and require no special treatment.
@@
 A recent paper by Taylor and Steigmann \cite{taylor2013two} reduces a bond based 3D plate to two dimensions with an integral through the plate's thickness.
-This creates a model that can represent thin structures and includes a bending term, but is used to simulate tension loading.
-The model is limited to the 3D bond-based Poisson ratio \(\nu=\sfrac{1}{4}\), though the same technique could be applied to a state-based model at the expense of complexity.
+This creates a model that can represent thin structures and includes a bending term, which resists transverse wrinkling behavior in a simulation of crack growth under tension loading.
+The model is limited to the 2D bond-based Poisson ratio \(\nu=\sfrac{1}{3}\), though the same technique could be applied to a state-based model at the expense of complexity.
 Outside of peridynamics, weakly nonlocal continuum mechanics models date to the work of Kr\"oner \cite{kroner1967elasticity} and of Eringen and Edelen \cite{eringen1972nonlocal}, and include higher-order displacement derivatives.
@@
 \label{sec:PDintro}
-Stewart Silling first developed the theory of peridynamics in~\cite{silling2000reformulation} to eliminate the problems associated with the undefined partial derivatives that attend the formation of cracks.
+Stewart Silling first developed the theory of peridynamics in~\cite{silling2000reformulation} to mitigate the problems associated with the undefined partial derivatives that attend the formation of cracks.
 The name refers to the force exerted on a point by material points a finite distance away.
@@
 
-To describe force functionals that incorporate the behavior of a totality of points in the nearby material (not just $\mathbf{x}$ and $\mathbf{q}$), we must introduce the concept of a peridynamic \emph{state}.
+To describe force functionals that incorporate the behavior of a totality of points in the nearby material (not just $\mathbf{x}$ and $\mathbf{q}$), we introduce the concept of a peridynamic \emph{state}.
 Introduced by Silling et al.\ \cite{silling2007peridynamic}, states are functions of the behavior of the continuum points surrounding each location.
@@
 With $i, j, k, l = 1,2$.
-For a circular $\omega$, combinations of $\{i,j,k,l\}$ with an odd number of any index, such as $\{1,1,1,2\}$ will integrate to 0.
+For a circular $\omega(\xi) = \omega(|\xi|)$, combinations of $\{i,j,k,l\}$ with an odd number of each index, such as $\{1,1,1,2\}$ or $\{2,1,2,2\}$, will result in odd powers of sine and cosine and integrate to 0.
 %
@@
 %
-Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced, $\Delta x$, throughout the entire plate, otherwise the displacement \(z(\mathbf{x}-\boldsymbol{\xi}_i)\) is ill-defined.
+Discretizing the bond-pair model as proposed above requires that nodes be evenly spaced, $\Delta x$, throughout the entire plate, otherwise the displacement \(z(\mathbf{x}-\boldsymbol{\xi}_i)\) is undefined.
 For this reason, the discretization does not allow for areas of higher and lower ``resolution''.
@@
 This convergence only continues to a minimum horizon, below which the discretized equation of motion (\cref{eq:discreteEoM}) ceases to accurately approximate the continuous integral formulation (\cref{eq:PDstateEoM,eq:SillingForceNO}).
-The minimum horizon size depends on the discretization; it appears that twice the node spacing is insufficient, and that three times the node spacing is sufficient.
-The difference is evident in \cref{fig:plate_minimum_h}.
+The minimum horizon size depends on the discretization; it appears that three times the node spacing is sufficient, but that a horizon that is only twice the node spacing is insufficient.
+The difference is evident in \cref{fig:plate_minimum_h}, which also shows that results are insensitive to fineness of discretization once the minimum horizon criterion is met.
 %
@@
   \centering
-  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_minimum_h.pgf}}
+%  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_minimum_h.pgf}}
+  \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_convergence_dx.pgf}}
   \caption{Horizon Must Include Sufficient Nodes}
@@
 Accurate results require a denser discretization than is the case for the elastic beams from previous work.
-\Cref{fig:plate_convergence_n} illustrates the model converging to the analytical solution as the discretization is made finer.
+\Cref{fig:plate_convergence_n} illustrates the model converging to the analytical solution as the discretization is made finer and the horizon shrinks.
 %
@@
   \resizebox{0.55\linewidth}{!}{\input{\plotpath/elasticPlate_convergence_n.pgf}}
-  \caption{The Bond-Pair Model Converges on Accurate Plate Deflection with Finer Dsicretization}
+  \caption{The Bond-Pair Model Converges on Accurate Plate Deflection with Finer Discretization}
   \label{fig:plate_convergence_n}
@@
 A demonstration of brittle fracture in a bending plate shows the potential of this model to broaden the class of problems that can realistically be modeled using peridynamics.
+\subsection*{Acknowledgements}
+This work was funded by grant number W911NF-11-1-0208 from the United States Air Force Office of Scientific Research.
 

### 2014-08-01 response/response.tex
Few small changes to response.tex
Also removed the PDF file from the repo so please rebuild.  If it worked
correctly, we should receive an email notifying us of this push.

@@
 Because readers are not yet accustomed to this sort of evaluation, especially for trigonometric and compound vector states, we feel that retaining the appendix is a solid compromise between keeping the body of the paper readable and allowing interested readers to quickly verify or imitate our derivations.
+Unless the reviewer insists upon it's removal, we prefer to keep it.
      \end{itemize}}
@@
         \quote{To create a plate model that also resists these deformations, i.e.
-a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from [10].}
+a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from [10].
+We use the adjective ``flat'' to indicate that, at least with consideration to the discretization chosen in this paper, a more complex discretization scheme will have to be utilized to accurately model ``curved shells''}
      \end{itemize}}
@@
         \end{quotation}
-        \item The focus of this paper is the model rather than the numerical methods, so we try to leave criticism of existing numerical methods to those working to remedy the situation.
-That said, using nonlocal vector calculus as the basis of an FEM would seem to handle nonlocality/scale effects, but risks reintroducing mesh dependence to failure analyses.
+    \item The focus of this paper is the physical model rather than the numerical methods; however, it is true that a conforming FEM would alleviate issues of convergence, linear patch test consistency, etc.
+it would also introduce the added difficulty of adaptively integrating to resolve discontinuities which is the primary attractiveness of the discretization we present as well as the theory of peridynamics in general.
      \end{itemize}}

### 2014-08-01 response/response.tex
revision submitted to IJSS

@@
 Because readers are not yet accustomed to this sort of evaluation, especially for trigonometric and compound vector states, we feel that retaining the appendix is a solid compromise between keeping the body of the paper readable and allowing interested readers to quickly verify or imitate our derivations.
-Unless the reviewer insists upon it's removal, we prefer to keep it.
+Unless the reviewer insists upon its removal, we prefer to keep it.
      \end{itemize}}
@@
         \item Shell models resist in-plane or membrane deformations, as opposed to plates, which resist only transverse deformations. This is noted on page 10:
-        \quote{To create a plate model that also resists these deformations, i.e.
+        \begin{quotation}To create a plate model that also resists these deformations, i.e.
 a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from [10].
-We use the adjective ``flat'' to indicate that, at least with consideration to the discretization chosen in this paper, a more complex discretization scheme will have to be utilized to accurately model ``curved shells''}
+        \end{quotation}
+          We use the adjective ``flat'' to indicate that, at least with consideration to the discretization chosen in this paper, a more complex discretization scheme will have to be utilized to accurately model ``curved shells''
      \end{itemize}}

### 2014-09-03 response/response_2.tex
added second response

\documentclass{article}
\usepackage[left=1.0in,right=1.0in,top=1.0in,bottom=1.0in]{geometry}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage[normalem]{ulem}
\usepackage{cancel}
\definecolor{light-gray}{gray}{0.5}

\begin{document}

\begin{center}
    {\LARGE \bf Point-by-Point Response to Reviewer's Comments} \\
     Author's Responses in {\color{red} Red}
\end{center}

%%%% First Reviewer %%%%
\section*{Reviewer Comments}
%

\begin{enumerate}
%
   \item I am not totally convinced by the authors arguments that the novelty of this paper is sufficiently high as to merit publication in IJSS. There are certainly differences from the approach used in [6], but I that these differences are largely algebraic and not conceptual. Certainly, it will require much tedious algebra to use the asymptotic expansion approach from [6] in a state-based setting. This method on the other hand has a critical difficulty that I pointed out in the first review but was not at all addressed in the response.

   {\color{red}
	It’s possible that we were not clear enough in the manuscript, but the differences between this paper and [6] are nearly entirely conceptual, stemming from a completely different way of characterizing bending. In this paper, bending is a fundamental deformation mode, i.e. there are forces that resist angle change, rather than the result of extension deformation that varies through the thickness, i.e. forces that resist only extension, but vary through the thickness. While it may not be the easiest way to represent thin plate bending, it opens the door for continuum analysis of materials that resist bending in different ways. For example, a graphene sheet only one atom thick resists bending without any thickness for displacement to vary along, and a lipid bilayer (sans inclusions) resists isotropic bending but does not resist deviatoric bending at all. Before moving on to these more exotic materials, it is necessary to first build up the simplest models, even if they don’t initially outperform the state of the art for the simplest problems. We started with the simplest possible bending model - the Euler beam in our previous paper [15], and this paper extends that work to the simplest 2D model - a Kirchhoff plate. The goal is that this model will serve as a foundation for models that hopefully outperform the state of the art in their ability to simulate bending behavior for new, complex materials, e.g. meta-materials.
	}
  \item In this paper, one has to compare with standard continuum models and do energy matching. Suppose one were in a situation where one is unsure of the correct continuum model (e.g. thick shells). Then what do we compare it with? The approach in [6] has no such issues.”

   {\color{red}
     The ability to model thick shells is an advantage of [6] over our work, just as the ability to model arbitrary Poisson’s ratios is an advantage of our work over [6]. That said, it just pushes the energy matching back one step, because the bond-based peridynamic solid model is produced by energy matching with a classical solid material. Please see Silling and Askari (2004), Equation 22, where the constitutive model used in [6] is clearly arrived at by energy matching. Other departures from Kirchhoff plate theory, such as nonlinear material behavior, are harder to incorporate with the thickness integral. For example, the damage model in [6] is a function of bottom-plane extension. If only the extension of the bottom surface is compared to a critical stretch, then downward curvature will never result in damage - the plate could be rolled into a cylinder without failing in one direction, and the same deformation in the opposite direction would produce failure. This is likely acceptable in a model that is used to handle bending components of a deformation that is primarily in-plane, but would have to be modified in a scenario where failure is expected to occur due to excessive bending. Moving the plane to the center or top only changes the type of bending that results in no extension of the tracked plane. This would also be a concern for damage that does not completely penetrate the plate. The model presented in this paper offers a way to handle failure in these scenarios.}
%
%
\end{enumerate}
%

\end{document}
